 
# Descriptive analysis  <a name="descriptive_analysis"></a>

This chapter is dedicated for all data-driven pharmacokinetics/pharmacodynmaic analysis, with a minimum level
of modeling.  Most often, the concentration-time profiles will be plotted, 
in both log- and linear-scale (see section \@ref(time-profile)).  A variety of visualization for PK-PD analyses are presented in section \@ref(descriptive-PKPD). 

First of all, a dataset (see below) needs to be loaded by using three different approaches mentioned earlier. If load sucessfully, the dataset will be populated in the subsequent sections in this chapter.  
 
 
```{r, eval=FALSE}
#----------------------------------------------------
# load_nmdat_container
#----------------------------------------------------
output$descriptive_analysis_data_selector <-renderUI({
   
  # callModule 
  #isolate({ 
    ALL = callModule(module_load_dataset, "load_nmdat_for_descriptive_analysis", 
                     ALL, dataset_name="mYtEsT_for_descriptive_analysis")
 # })
  
  # UI  
  fluidRow(column(6, 
                   module_load_dataset_UI(id="load_nmdat_for_descriptive_analysis", label=NULL)
                 ), 
            column(6, 
                   HTML(colFmt("internal library: build-in dataset <br>
                                within session: secondary data derived from the original <br> 
                                external file: external file", color="gray")
                        )
                   )
            )  
  })
  
tagList(
  fluidRow(column(width=12, tags$hr(style="border-color: gray;"))),
  fluidRow(column(width=12, uiOutput(("descriptive_analysis_data_selector")))), 
  fluidRow(column(width=12, tags$hr(style="border-color: gray;")))
)
```


## Time profile {#time-profile}    

The concentration-time profiles are the most commonly used visualization for both PK or PD. 
If your dataset were standardized previously, you should be able to generate these time-profiles using 
the scripts below. The general step-by-step instructions were shown below: 

1. As mentioned early, the loaded dataset is presented in the tab of *dataset*. 
Within the tab, some commonly used filters is shown and they could be used to narrow down your dataset. 
For examples, select either one study or multiple studies, select which analyte and which dose groups.
Note you can only choose one analye; you may choose multiple analytes at next section \@ref(descriptive-PKPD).

2. In the tab of *script*, you may select/run/modify the template scripts and generate the derived data(s), table(s) and figure(s) based on the input data (dataset) with/withou the parameters (params). Note, certain key words should be reserved; certain formatting should be followed. See instruction carefully.

3. The resulting *data*, *table*, and *figure* (if ever generated) will be presented in the corresponding tab. You may save or download them accordingly.
 

```{r}
drug_descriptive_analysis_inputData <- reactive({
  tdata = ALL$DATA[["mYtEsT_for_descriptive_analysis"]] 
  validate(need(tdata, message="no data found yet")
  )
  tdata
  
  # also include dosing event (TEST=NA), NEED EXTRT FROM ADEX
  # tdata %>% filter(
  #   TEST %in% c(NA, input$which_test), 
  #   ARMA %in% input$which_arma
  # ) 
  
})
```

```{r}  
 
output$descriptive_time_profile <- renderUI({ 

  #validate(need(drug_descriptive_analysis_inputData(), message="no data found yet"))
 
  # scripts
  script <- list.files(path=paste0(HOME, "/script/"), 
                         full.names = TRUE,
                         pattern="descriptive_time_profile")
  names(script) = basename(script)
    
  # callModule
  ALL = callModule(module_run_script, "descriptive_time_profile", 
                   ALL, 
                   dataset=NULL, #drug_descriptive_analysis_inputData(), 
                   #dataset_name = "mYtEsT_for_descriptive_analysis",
                   script=script)
    
  # UI
  module_run_script_UI(("descriptive_time_profile"), label = NULL) 
     
})

 fluidRow(column(12, uiOutput(("descriptive_time_profile"))))

```
 

 






```{r, eval=FALSE}
  #----------------------------------------------------------------------------
  # Version 0.1   Created on 11/08/2018, Feng Yang
  # 
  #----------------------------------------------------------------------------
  # Input
  # -----------------
  # 1) nmdat:  meta data file 
  #
  #
  # Output Figures: 
  #------------------
  # PK 
  # 1) Mean PK profile (log-scale and linear scale, by panel or not)
  # 2) Individual PK profile (log-scale and linear scale, by panel or not)
  # 
  # Target
  # 3) Mean Target profile (log-scale and linear scale, by panel or not)
  # 4) Individual Target profile (log-scale and linear scale, by panel or not)
  
  # PD Response
  # 5) Mean response (raw) profile (log-scale and linear scale, by panel or not)
  # 6) Individual response (raw) profile (log-scale and linear scale, by panel or not) 
  # 7) Mean response (PCHG) profile (log-scale and linear scale, by panel or not)
  # 8) Individual response (PCHG) profile (log-scale and linear scale, by panel or not) 
  #----------------------------------------------------------------------------
  # 
  
  if (idebug ==1) {
    FIGURE_ALL = NULL
    TABLE_ALL = NULL
    LISTING_ALL = NULL
  }

  
  ##########################################################################################
  # load nmdat for all subsequent analysis 
  ##########################################################################################
     
   
    
  
  ##########################################################################################
  # individual PK plot
  ##########################################################################################
  
  # data: 
  #---------- 
  tdata = nmdat %>% filter(TEST==PK.TEST.NAME, TIME>=0) %>% 
    mutate(TIME=as_numeric(TIME), 
           DVOR = ifelse(as_numeric(DVOR)<as_numeric(LLOQ), as_numeric(LLOQ)/2, as_numeric(DVOR)))
         
  # plot: 
  #---------- 
  x=setup_axis(xscale='7_14', xlimits=c(0, max(tdata$TIME, na.rm=TRUE)))
  
  fig = ggplot(tdata , aes(x=TIME, y=DVOR, group=USUBJID, col=ARMA)) + 
    #ggtitle("Concentration Time Profile") + 
    
    geom_point() + geom_line() + 
    
    scale_color_manual(values=palette()) + 
    
    scale_x_continuous(breaks=x$breaks, label=x$labels) +
    #scale_x_continuous(trans=‘log2’), scale_y_continuous(trans=‘log2’) : another allowed value for the argument trans is ‘log10’
    
    scale_y_log10(breaks = 10^(seq(-1,3,by=1)), #trans_breaks("log10", function(x) 10^x),
                  labels = 10^(seq(-1,3,by=1))) + # trans_format("log10", math_format(10^.x))) +
    
    #coord_trans( y="log10") +   # possible values for x and y are “log2”, “log10”, “sqrt”, …

    #coord_cartesian(xlim = c(0, 85)) + 
    
    xlab("Time (day)") + 
    ylab(paste0("Concentration of ", PK.TEST.LABEL, " (mg/L)")) +   
      
    theme_bw() + base_theme(font.size = as.integer(12)) + 
    guides(col=guide_legend(ncol=4,byrow=TRUE)) 
  
  # individual log scale 
  fig = fig + annotation_logticks(sides ="l")  +   # "trbl", for top, right, bottom, and left.
    geom_hline(yintercept=c(0.078), lty="dashed") + 
    geom_text(y=log10(0.1 ), x=7, aes(label="BLQ=0.078 mg/L", hjust=0), size=3,    color='black')  
  
  attr(fig, 'title') <- paste0("Individual Log-scaled Concentration of ", PK.TEST.NAME, " in Serum vs Actual Sampling Day Following Subcutaneous or Intravenous Dose(s) of ", PK.TEST.NAME, " (", STUDY.NAME, ")")
  FIGURE_ALL[["PK_INDIV_LOG"]] = fig
  
  # individual log scale by panel
  fig = fig + facet_wrap(~ARMA) + ggplot2::theme(legend.position = "none")  
  attr(fig, 'title') <- paste0("Individual Log-scaled Concentration of ", PK.TEST.NAME, " in Serum vs Actual Sampling Day Following Subcutaneous or Intravenous Dose(s) of ", PK.TEST.NAME, " (", STUDY.NAME, ")")
  attr(fig, 'width') <- 8
  attr(fig, 'height') <- 6
  FIGURE_ALL[["PK_INDIV_LOG_PANEL"]] = fig 
  fig
  
  
  
  ##########################################################################################
  # Mean+SE TARGET time profile
  ##########################################################################################
   
  fig = empty_canvas(label="TARGET Data Visualization"); 
  attr(fig, 'title') <- ""
  FIGURE_ALL[["canvas_std_TARGET_visualization"]] = fig  
  
  # data: 
  #---------- 
  tdata = nmdat   #%>% filter(is.na(as_numeric(EXTDOSE)))  # remove all dosing events
  
  tdata = tdata %>% filter(TEST==TARGET.TEST.NAME)  %>%    # exclude pre-dose samples
    
    #Concentrations below the lower limit of quantification (LLOQ = 0.078 mg/L) are set to LLOQ/2 
    mutate(DVOR = ifelse(DVOR<LLOQ, LLOQ/2, DVOR))  %>% 
    
    # calculate the statistics (Mean, SE, SD)
    calc_stats(id="USUBJID", 
               group_by=c("STUDYID", "TEST","ARMA","ARMAN","NTIM","TIMEPT"), 
               value="DVOR") %>% 
    
    # ARMA = ARMA + (N)
    arrange(ARMAN) %>% group_by(ARMA) %>% 
    mutate(ARMA2 = paste0(ARMA, "(", max(N), ")")) %>% ungroup() %>%   # Note use Max(N)
    mutate(ARMA = ordered(ARMA2, levels=unique(as.character(ARMA2)))) %>%
    
    select(STUDYID, TEST, ARMA, NTIM, TIMEPT, N, Mean, meanMinusSE, meanPlusSE, Mean_SD, SE, Median_Range) %>% 
    arrange(TEST, ARMA, NTIM)
  
  
  # plot
  #------- 
  x=setup_axis(xscale='7_14', xlimits=c(0, max(tdata$NTIM, na.rm=TRUE)))
  #y=setup_axis(xscale='100_200', xlimits=c(0, max(tdata$meanPlusSE, na.rm=TRUE)))
  
  # no pre-dose samples in plot
  fig = ggplot(tdata, aes(x=NTIM, y=Mean, group=ARMA, col=ARMA)) + 
    #ggtitle("Concentration Time Profile") + 
    
    geom_point() + geom_line() +   
    geom_errorbar(aes(ymin = meanMinusSE, ymax = meanPlusSE), width=2) + 
    
    scale_color_manual(values=palette()) +  # values = c("black", "blue", "green")) + 
    
    scale_x_continuous(breaks=x$breaks, label=x$labels) +
    #scale_y_continuous(breaks=y$breaks, label=y$labels) +
    
    #coord_cartesian(xlim = c(0, 85)) + 
    
    xlab("Time (day)") +  
    ylab(paste0("Concentration(SE) of ", TARGET.TEST.LABEL, " (mg/L)")) +   
    
    theme_bw() + base_theme(font.size = as.integer(12)) + 
    guides(col=guide_legend(ncol=4,byrow=TRUE))    
  
  #geom_hline(yintercept=c(4.9, 27.8, 0.039), lty="dashed") + 
  #geom_text(y=log10(24 ), x=112, aes(label="27.8 mg/L", hjust=0),   color='black')  
  
  fig
  
  # linear scale
  attr(fig, 'title') <- paste0("Mean (±SE) Concentration of ", TARGET.TEST.LABEL, " in Serum vs Nominal Sampling Day Following Subcutaneous or Intravenous Dose(s) of ", PK.TEST.NAME, " (", STUDY.NAME, ")")
  FIGURE_ALL[["TARGET_MEAN_LN"]] = fig 
   
  # log scale 
  # Typically, no log-scale needed for target
  
  # listing table
  tabl = tdata %>% select(TEST, ARMA, TIMEPT, NTIM, Mean_SD, SE) 
  attr(tabl, 'title') <-  paste0("Descriptive Statistics of ", TARGET.TEST.LABEL, " in Serum ", "(", STUDY.NAME, ")")
  LISTING_ALL[["TARGET_MEAN"]] = tabl
   
  
  ##########################################################################################
  # individual TARGET time profile
  ##########################################################################################
   
  # data: 
  #---------- 
  tdata = nmdat %>% filter(TEST==TARGET.TEST.NAME, TIME>=0) %>% 
    mutate(TIME=as_numeric(TIME), 
           DVOR = ifelse(as_numeric(DVOR)<as_numeric(LLOQ), as_numeric(LLOQ)/2, as_numeric(DVOR)))
  
  # plot: 
  #---------- 
  x=setup_axis(xscale='7_28', xlimits=c(0, max(tdata$TIME)))
  
  fig = ggplot(tdata , aes(x=TIME, y=DVOR, group=USUBJID, col=ARMA)) + 
    #ggtitle("Concentration Time Profile") + 
    
    geom_point() + geom_line() + 
    
    scale_color_manual(values=palette()) + 
    
    scale_x_continuous(breaks=x$breaks, label=x$labels) +
    #scale_x_continuous(trans=‘log2’), scale_y_continuous(trans=‘log2’) : another allowed value for the argument trans is ‘log10’
    
    #scale_y_log10(breaks = 10^(seq(-1,3,by=1)), #trans_breaks("log10", function(x) 10^x),
    #              labels = 10^(seq(-1,3,by=1))) + # trans_format("log10", math_format(10^.x))) +
    
    #coord_trans( y="log10") +   # possible values for x and y are “log2”, “log10”, “sqrt”, …
    
    #coord_cartesian(xlim = c(0, 85)) + 
    
    xlab("Time (day)") + 
    ylab(paste0("Concentration of ", TARGET.TEST.LABEL, " (mg/L)")) +   
    
    theme_bw() + base_theme(font.size = as.integer(12)) + 
    guides(col=guide_legend(ncol=4,byrow=TRUE)) 
  
  # attr(fig, 'title') <- paste0("Individual Concentration-time Profiles of ", TARGET.TEST.LABEL, " By Dose Group")
  # FIGURE_ALL[["ARGET_INDIV"]] = fig 
  
  fig = fig + facet_wrap(~ARMA)+ ggplot2::theme(legend.position = "none")
  attr(fig, 'title') <-  paste0("Individual Concentration of ", TARGET.TEST.LABEL, " in Serum vs Actual Sampling Day Following Subcutaneous or Intravenous Dose(s) of ", PK.TEST.NAME, " (", STUDY.NAME, ")")
  attr(fig, 'width') <- 8
  attr(fig, 'height') <- 6
  FIGURE_ALL[["TARGET_INDIV_LN_PANEL"]] = fig 
  fig
  
  
  
  
  ##########################################################################################
  # mean PD  profiles
  ##########################################################################################
  fig = empty_canvas(label=paste0(PD.TEST.LABEL, " Data Visualization")); 
  attr(fig, 'title') <- ""
  FIGURE_ALL[["canvas_PD_Visualization"]] = fig  
   
  # data: 
  #---------- 
  tdata = nmdat   #%>% filter(is.na(as_numeric(EXTDOSE)))  # remove all dosing events
  tdata = tdata %>% filter(TEST==PD.TEST.NAME)  %>%    # exclude pre-dose samples
    
    #Concentrations below the lower limit of quantification (LLOQ = 0.078 mg/L) are set to LLOQ/2 
    #mutate(DVOR = ifelse(DVOR<LLOQ, LLOQ/2, DVOR))  %>% 
    
    # calculate the statistics (Mean, SE, SD)
    calc_stats(id="USUBJID", 
               group_by=c("STUDYID", "TEST","ARMA","ARMAN","NTIM","TIMEPT"), 
               value="DVOR") %>% 
    
    # ARMA = ARMA + (N)
    arrange(ARMAN) %>% group_by(ARMA) %>% 
    mutate(ARMA2 = paste0(ARMA, "(", max(N), ")")) %>% ungroup() %>%   # Note use Max(N)
    mutate(ARMA = ordered(ARMA2, levels=unique(as.character(ARMA2)))) %>%
    
    select(STUDYID, TEST, ARMA, NTIM, TIMEPT, N, Mean, meanMinusSE, meanPlusSE, Mean_SD, SE, Median_Range) %>% 
    arrange(TEST, ARMA, NTIM)
  
  
  # plot
  #------- 
  
  x=setup_axis(xscale='7_14', xlimits=c(0, max(tdata$NTIM, na.rm=TRUE)))
  y=setup_axis(xscale='25_50', xlimits=c(0, max(tdata$meanPlusSE, na.rm=TRUE)))
  
  fig = ggplot(tdata , aes(x=NTIM, y=Mean, group=ARMA, col=ARMA)) +
    #ggtitle("Concentration Time Profile") + 
    
    geom_point() + geom_line() + 
    geom_errorbar(aes(ymin = meanMinusSE, ymax = meanPlusSE), width=2)  + 
    
    scale_color_manual(values=palette()) + 
     
    scale_x_continuous(breaks=x$breaks, label=x$labels) +
    scale_y_continuous(breaks=y$breaks, label=y$labels) +  
  
    xlab("Time (day)") + 
    ylab(paste0("Mean(SE) of ", PD.TEST.LABEL, " (U/mL)")) + 
    
    #coord_cartesian(xlim = c(0, 85)) + 
    theme_bw() +  base_theme(font.size = as.integer(12)) + 
    guides(col=guide_legend(ncol=4,byrow=TRUE))  
     
  
  fig
   
  attr(fig, 'title') <- paste0("Mean (±SE) ", PD.TEST.LABEL, " vs Nominal Sampling Day Following Subcutaneous or Intravenous Dose(s) of ", PK.TEST.NAME, " (", STUDY.NAME, ")")
  FIGURE_ALL[["PD_MEAN_LN"]] = fig  
  
    
  tabl = tdata %>% select(TEST, ARMA, TIMEPT, NTIM, Mean_SD, SE) 
  attr(tabl, 'title') <-  paste0("Descriptive Statistics of ", PD.TEST.LABEL,  "(", STUDY.NAME, ")")
  LISTING_ALL[["PD_MEAN"]] = tabl
  
  
  ##########################################################################################
  # Indiv PD  profiles
  ##########################################################################################
  # data: 
  #---------- 
  tdata = nmdat %>% filter(TEST==PD.TEST.NAME, TIME>=0)  %>% 
        mutate(TIME=as_numeric(TIME), 
               DVOR = as_numeric(DVOR))
  
  # plot: 
  #---------- 
  x=setup_axis(xscale='7_28', xlimits=c(0, max(tdata$NTIM, na.rm=TRUE)))
  y=setup_axis(xscale='50_100', xlimits=c(0, max(tdata$DVOR, na.rm=TRUE)))
  
  fig = ggplot(tdata , aes(x=TIME, y=DVOR, group=USUBJID, col=ARMA)) + 
    #ggtitle("Concentration Time Profile") + 
    
    geom_point() + geom_line() + 

    scale_color_manual(values=palette()) + 
    
    scale_x_continuous(breaks=x$breaks, label=x$labels) +
    scale_y_continuous(breaks=y$breaks, label=y$labels) +  
  
    xlab("Time (day)") + 
    ylab(paste0(PD.TEST.LABEL, " (U/mL)")) + 
    
    #coord_cartesian(xlim = c(0, 85)) + 
    theme_bw() + base_theme(font.size = as.integer(12)) + 
    guides(col=guide_legend(ncol=4,byrow=TRUE))  
     
  fig
  
  # attr(fig, 'title') <- paste0("Individual Time Profiles of ", PD.TEST.LABEL, " By Dose Group")
  # FIGURE_ALL[["PD_INDIV"]] = fig  
  
  
  fig = fig + facet_wrap(~ARMA) + ggplot2::theme(legend.position = "none")
  attr(fig, 'title') <- paste0("Inividual ", PD.TEST.NAME, " vs Actual Sampling Day Following Subcutaneous or Intravenous Dose(s) of ", PK.TEST.NAME, " (", STUDY.NAME, ")")
  attr(fig, 'width') <- 8
  attr(fig, 'height') <- 6
  FIGURE_ALL[["PD_INDIV_LN_PANEL"]] = fig 
  fig
  
    
  
  ##########################################################################################
  # mean PCHG OF PD profiles
  ##########################################################################################
    
  # data: 
  #---------- 
  tdata = nmdat   #%>% filter(is.na(as_numeric(EXTDOSE)))  # remove all dosing events  
  tdata = tdata %>% filter(TEST==PD.TEST.NAME)  %>%    # exclude pre-dose samples
    
    # use PCHG as DVOR
    mutate(DVOR = as_numeric(PCHG),   # the key
           NTIM = as_numeric(NTIM))  %>% 
    
    # calculate the statistics (Mean, SE, SD)
    calc_stats(id="USUBJID", 
               group_by=c("STUDYID", "TEST","ARMA","ARMAN","NTIM","TIMEPT"), 
               value="DVOR") %>% 
    
    # ARMA = ARMA + (N)
    arrange(ARMAN) %>% group_by(ARMA) %>% 
    mutate(ARMA2 = paste0(ARMA, "(", max(N), ")")) %>% ungroup() %>%   # Note use Max(N)
    mutate(ARMA = ordered(ARMA2, levels=unique(as.character(ARMA2)))) %>%
    
    select(STUDYID, TEST, ARMA, NTIM, TIMEPT, N, Mean, meanMinusSE, meanPlusSE, Mean_SD, SE, Median_Range) %>% 
    arrange(TEST, ARMA, NTIM)
  
  # plot
  #-------  
  x=setup_axis(xscale='7_14', xlimits=c(0, max(tdata$NTIM, na.rm=TRUE)))
  y=setup_axis(xscale='25_25', xlimits=c(-100, 50))  #range(c(meanMinusSE, meanPlusSE)) 
  
  fig = ggplot(tdata , aes(x=NTIM, y=Mean, group=ARMA, col=ARMA)) + 
    #ggtitle("Concentration Time Profile") + 
    
    geom_point() + geom_line() + 
    geom_errorbar(aes(ymin = meanMinusSE, ymax = meanPlusSE), width=2)  + 
    
    scale_color_manual(values=palette()) + 
      
    scale_x_continuous(breaks=x$breaks, label=x$labels) +
    scale_y_continuous(breaks=y$breaks, label=y$labels) +
    #coord_cartesian(xlim = c(0, 85)) + 
    
    xlab("Time (day)") + 
    ylab(paste0("Percent Change(SE) from Baseline (", PD.TEST.LABEL, ")")) + 

    theme_bw() + base_theme(font.size = as.integer(12)) + 
    guides(col=guide_legend(ncol=4,byrow=TRUE))   
  
  fig
  
   
  attr(fig, 'title') <-paste0("Mean (±SE) ", PD.PCHG.LABEL, " vs Nominal Sampling Day Following Subcutaneous or Intravenous Dose(s) of ", PK.TEST.NAME, " (", STUDY.NAME, ")")
  FIGURE_ALL[["PD_PCHG_MEAN_LN"]] = fig 
   
  tabl = tdata %>% select(STUDYID, TEST, ARMA, TIMEPT, NTIM, Mean_SD, SE) 
  attr(tabl, 'title') <-  paste0("Descriptive Statistics of ", PD.PCHG.LABEL,  "(", STUDY.NAME, ")")
  LISTING_ALL[["PD_PCHG_MEAN"]] = tabl
  
  
  ##########################################################################################
  # individual PCHG PD plot 
  ##########################################################################################
  
  # data: 
  #---------- 
  tdata = nmdat   #%>% filter(is.na(as_numeric(EXTDOSE)))  # remove all dosing events  
  tdata = tdata %>% filter(TEST==PD.TEST.NAME)  %>%    # exclude pre-dose samples
    
    # use PCHG as DVOR
    mutate(DVOR = as_numeric(PCHG),   # the key
           NTIM = as_numeric(NTIM)) 
  
  # plot
  #-------
  x=setup_axis(xscale='7_28', xlimits=c(0, max(tdata$TIME, na.rm=TRUE)))
  y=setup_axis(xscale='25_50', xlimits=range(tdata$DVOR))
  
  fig = ggplot(tdata, aes(x=TIME, y=DVOR, group=USUBJID, col=ARMA)) + 
    #ggtitle("Concentration Time Profile") + 
    
    geom_point() + geom_line() + 
    #geom_errorbar(aes(ymin = meanMinusSE, ymax = meanPlusSE), width=2)  + 
    
    scale_color_manual(values=palette()) + 
     
    scale_x_continuous(breaks=x$breaks, label=x$labels) +
    scale_y_continuous(breaks=y$breaks, label=y$labels) +
    
    #coord_cartesian(xlim = c(0, 85)) + 
    
    xlab("Time (day)") + 
    ylab(paste0("Percent Change from Baseline (", PD.TEST.LABEL, ")")) + 
     
    theme_bw() + base_theme(font.size = as.integer(12)) + 
    guides(col=guide_legend(ncol=4,byrow=TRUE))   
   
  fig = fig + facet_wrap(~ARMA) + ggplot2::theme(legend.position = "none")
  attr(fig, 'title') <- paste0("Inividual ", "Percent Change from Baseline in CH50", " vs Actual Sampling Day Following Subcutaneous or Intravenous Dose(s) of ", PK.TEST.NAME, " (", STUDY.NAME, ")")
  attr(fig, 'width') <- 8
  attr(fig, 'height') <- 6
  FIGURE_ALL[["PD_PCHG_INDIV_LN_PANEL"]] = fig
  fig
  
   
  ###########################################
  # print to word and ppt
  ###########################################
  
  if (idebug ==1) { 
  
    # use customized version
    myppt <- pptx(title = "title", template = '~/FYANG/LIB/pptTemplate.pptx')
    mydoc <- docx(template = "~/FYANG/LIB/memoTemplate.docx", empty_template = FALSE)
    
    tt = print2_word_ppt(FIGURE_ALL, TABLE_ALL,  mydoc, myppt) 
    
    writeDoc(tt$mydoc, file = './docs/memo_results.docx')
    
    writeDoc(tt$myppt, file = './docs/ppt_results.pptx')
    
  }
  
    
  



```
 
