---
title: "An Interactive Handbook for Pharmacometrics Analysis"
author: "Feng Yang"
date: "12/18/2018"
output:
  html_document:
    code_folding: show
    fig_caption: yes
    keep_md: no
    number_sections: yes
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: yes
      smooth_scroll: yes
resource_files:
- rmd/01_preface/01_preface.Rmd
- rmd/02_construct_dataset/01_construct_dataset.Rmd
- rmd/03_integrity_check/01_load_data.Rmd
- rmd/03_integrity_check/02_quick_check.Rmd
- rmd/03_integrity_check/03_advanced_check.Rmd
- rmd/03_integrity_check/04_buildIn_model.Rmd
- rmd/04_summary_dataset/01_summary_dataset.Rmd
- rmd/05_descriptive_analysis/01_stdtimeprofile.Rmd
- rmd/05_descriptive_analysis/02_pkpd_relationship.Rmd
- rmd/05_descriptive_analysis/03_NCA_analysis.Rmd
- rmd/06_run_ctl/01_run_nonmem_model.Rmd
- rmd/06_run_ctl/02_model_diagnostic.Rmd
- rmd/07_run_cpp/01_run_sim.Rmd
- rmd/08_exposure_response/01_exposure_response.Rmd
- rmd/09_advanced_model/01_advanced_model.Rmd
- rmd/10_reporting/01_reporting.Rmd
- rmd/90_appendix/01_global_setting.Rmd
- rmd/90_appendix/01_global_variable_notused.Rmd
- rmd/90_appendix/01_model_library.Rmd
- rmd/90_appendix/02_dplyr.Rmd
- rmd/90_appendix/03_ggplot.Rmd
- rmd/90_appendix/04_mrgsolve.Rmd
- rmd/90_appendix/05_tools.Rmd 
- rmd/references.Rmd
- module/module_build_dataset.R
- module/module_build_dataset_wrapper.R
- module/module_check_nmdat_status.R
- module/module_checkInCols.R
- module/module_checkInRows.R
- module/module_checkOut.R
- module/module_fetch_job.R
- module/module_ggplot_brush.R
- module/module_linked_profiles.R
- module/module_load_cppModel.R
- module/module_load_ctlModel.R
- module/module_load_data.R
- module/module_load_dataset.R
- module/module_model_diagnostic_predefined.R
- module/module_review.R
- module/module_review_cppModel.R
- module/module_review_ctlModel.R
- module/module_review_script.R
- module/module_run_script.R
- module/module_runsim.R
- module/module_runsim_adex.R
- module/module_runsim_adsl.R
- module/module_runsim_ouput.R
- module/module_runsim_setting.R
- module/module_save_data.R
- module/module_save_figure.R
- module/module_save_table.R
- module/module_submit_job.R
- module/module_tabBox_next_previous.R
- module/module_table_output.R
- module/module_update_cppModel.R
- module/module_update_ctlModel.R
- module/module_visnetwork.R
- module/module_visnetwork_model_development.R
- module/module_visnetwork_model_library.R
- script/build_adex.R
- script/build_adpc.R
- script/build_adpx.R
- script/build_adsl.R
- script/build_nmdat.R
- script/descriptive_PKPD_hysterisis.R
- script/descriptive_PKPD_sigmoid.R
- script/descriptive_time_profile_indiv.R
- script/descriptive_time_profile_mean.R
- script/runSim_by_script.R
- script/simdata_pct_threshold.R
- script/simdata_plot_VPC.R
- script/simdata_summary_exposure.R
- script/simdata_summary_exposure_v2.R
- script/user_specified_diagnostic_plot_GOF1.R
- script/user_specified_diagnostic_plot_GOF2.R
- script/user_specified_diagnostic_plot_GOF3.R
- script/xpdb_diagnostic_ETAvsCOV.R
- script/xpdb_diagnostic_ETAvsETA.R
- script/xpdb_diagnostic_GOF1.R
- script/xpdb_diagnostic_GOF2.R
- script/xpdb_diagnostic_GOF3.R
- data/adex.csv
- data/adsl.csv
- data/adpc.csv
- data/other.csv
- data/nmdatPK.csv
- data/nmdatPKPD.csv
- ctl/LN001.ctl
- ctl/LN002.ctl
- ctl/MM001.ctl
- cpp/library/effect.cpp
- cpp/library/emax.cpp
- cpp/library/modpk2po.cpp
- cpp/library/pk1cmt.cpp
- cpp/library/pk2cmt.cpp
- cpp/library/pk3cmt.cpp
- cpp/library/pkpdExample.cpp
- cpp/library/popex.cpp
- cpp/library/popExample.cpp
- cpp/library/tmdd.cpp
- cpp/LN001.cpp
- cpp/MM001.cpp
- lib/pkmeta.xlsx
- lib/pkmeta_old.xlsx
- util/ggplot/add_formula_pvalue.R
- util/ggplot/base_histgram.r
- util/ggplot/base_scatter.r
- util/ggplot/base_theme.R
- util/ggplot/cat_boxplot.R
- util/ggplot/doublePanelPlot.r
- util/ggplot/doubleYPlot.r
- util/ggplot/ggpaircor.R
- util/ggplot/multiplot.R
- util/ggplot/setup_scale.R
- util/ggplot/zzz.r
- util/modeldev/all_function.R
- util/modeldev/check_run_status.R
- util/modeldev/fetch_job_from_HPC.R
- util/modeldev/list_folder_on_HPC.R
- util/modeldev/read_runno.R
- util/modeldev/read_runSummary_table.R
- util/modeldev/run_command_on_HPC.R
- util/modeldev/submit_job_to_HPC.R
- util/modeldev/util_dev.r
- util/mrgsolve/create_event.R
- util/mrgsolve/event_add_adsl.R
- util/mrgsolve/process_event.R
- util/mrgsolve/runSim_by_dosing_regimen.R
- util/mrgsolve/sim_timept.R
- util/mrgsolve/util_sim.r
- util/nmdat/extract_nmdat_name.R
- util/nmdat/fillUpCol_df.R
- util/nmdat/fuzzy_match.R
- util/nmdat/parseARMA.R
- util/nmdat/parseExpr.R
- util/nmdat/parseTIMEPT.R
- util/nmdat/read_datafile.R
- util/nmdat/standardise_SAMDTTM.R
- util/nmdat/standardise_USUBJID.R
- util/pkparams/calc_half_life.R
- util/pkparams/util_pk.r
- util/reporteR/addParagraph2.R
- util/reporteR/docAcctTab.r
- util/reporteR/docCoverPage.r
- util/reporteR/docPKPD.r
- util/reporteR/docStdProfile.r
- util/reporteR/myFlexTable.R
- util/reporteR/print_title_footnote.R
- util/reporteR/print2_word_ppt.R
- util/reporteR/vanilla_table.R
- util/rmarkdown/runAllChunks.R
- util/shinyPMx/best_guess.R
- util/shinyPMx/determineCurrentUser.R
- util/shinyPMx/plotIt.R
- util/stat/basic_stats.R
- util/stat/calc_stats.R
- util/stat/summary_of_studies.R
- util/util/add_prefix.R
- util/util/as_numeric.R
- util/util/as_time.R
- util/util/assign_Q.R
- util/util/colAttr.R
- util/util/colFmt.R
- util/util/colScheme.R
- util/util/convert_vars_type.R
- util/util/empty_canvas.R
- util/util/lmp.R
- util/util/merge_all.R
- util/util/order_cols.R
- util/util/spread_n.R
- util/util/strVec2matrix.R
- util/util/try_eval.R
- util/util/u_find_first_occurrence.R
- util/util/u_signif.R
- util/util/util.r
- util/xpose/GOF_PD1.R
- util/xpose/util_xpose.r

runtime: shiny
pdf_document:
  fig_caption: yes
  keep_tex: yes
  toc: yes
  toc_depth: 3
---


```{r, eval=FALSE}
#----------------------------------------
# to create the list of resource_files
#----------------------------------------
source("./global.R")
HOME <- paste0(".") 

file.lst = NULL
file.lst <- c(file.lst, list_files_in_a_folder(folder.loc=paste0(HOME, "/rmd/"), file.extension=c(".Rmd")))
file.lst <- c(file.lst, list_files_in_a_folder(folder.loc=paste0(HOME, "/module/"), file.extension=c(".r", ".R")))
file.lst <- c(file.lst, list_files_in_a_folder(folder.loc=paste0(HOME, "/script/"), file.extension=c(".r", ".R")))
file.lst <- c(file.lst, list_files_in_a_folder(folder.loc=paste0(HOME, "/data/"), file.extension=c(".csv")))
file.lst <- c(file.lst, list_files_in_a_folder(folder.loc=paste0(HOME, "/ctl/"), file.extension=c(".ctl")))
file.lst <- c(file.lst, list_files_in_a_folder(folder.loc=paste0(HOME, "/cpp/"), file.extension=c(".cpp")))
file.lst <- c(file.lst, list_files_in_a_folder(folder.loc=paste0(HOME, "/lib/"), file.extension=c(".xlsx", "pptx", "docx")))
file.lst <- c(file.lst, list_files_in_a_folder(folder.loc=paste0(HOME, "/util/"), file.extension=c(".r", ".R")))

# find a string multiple files
if (1==2) { 
    for (ifile in 1:length(file.lst)) {
     print(file.lst[ifile])
     txt = paste0(readLines(file.lst[ifile]), collapse=" ")
     if ( length(grep("abc", txt, fixed=TRUE) )) {        #  reshape sm
       print(file.lst[ifile])
       print("found one")
       
       exit;
     }
    }
}
 
file.lst <- gsub("./", " - ", file.lst, fix=TRUE)
file.lst <- gsub("//", "/", file.lst, fix=TRUE)
file.lst <- paste0(file.lst, collapse = "\n")

write_csv(data.frame(file.lst), path="tmp.txt")
 

```





```{r, setup, include=FALSE}
#----------------------------------------
# to reload R file in case updating
#----------------------------------------

#HOME <- paste0(getwd(), "/")
HOME = paste0(normalizePath("."), "/")
 
source("./global.R")

file.lst <- list_files_in_a_folder(folder.loc=paste0(HOME, "/util/"), file.extension=c(".r", ".R"))
for (ifile in 1:length(file.lst)) {source(file=file.lst[ifile]) }     

file.lst <- list_files_in_a_folder(folder.loc=paste0(HOME, "/module/"), file.extension=c(".r", ".R"))
for (ifile in 1:length(file.lst)) {source(file=file.lst[ifile])  }     
 
file.lst <- list_files_in_a_folder(folder.loc=paste0(HOME, "/script/"), file.extension=c(".r", ".R"))
for (ifile in 1:length(file.lst)) {source(file=file.lst[ifile])  }     

```


 
 
```{r}

ALL <- reactiveValues(
  DATA   = default_DATA, 
  FIGURE = default_FIGURE, 
  TABLE = default_TABLE, 
  cppModel = default_cppModel, 
  ctlModel = default_ctlModel, 
  script = default_script
)  
```



```{r eval=FALSE}
rmd <- list.files(pattern = '*.Rmd', recursive = T)
chunks <- paste0("```{r child = './", rmd, "'}\n```\n")
cat(chunks, sep = '\n')
```
 

```{r child = './rmd/01_preface/01_preface.Rmd'}
```

```{r child = './rmd/02_construct_dataset/01_construct_dataset.Rmd'}
```

```{r child = './rmd/03_integrity_check/01_load_data.Rmd'}
```

```{r child = './rmd/03_integrity_check/02_quick_check.Rmd'}
```

```{r child = './rmd/03_integrity_check/03_advanced_check.Rmd'}
```

```{r child = './rmd/03_integrity_check/04_buildIn_model.Rmd'}
```

```{r child = './rmd/04_summary_dataset/01_summary_dataset.Rmd'}
```

```{r child = './rmd/05_descriptive_analysis/01_stdtimeprofile.Rmd'}
```

```{r child = './rmd/05_descriptive_analysis/02_pkpd_relationship.Rmd'}
```

```{r child = './rmd/05_descriptive_analysis/03_NCA_analysis.Rmd'}
```

```{r child = './rmd/06_run_ctl/01_run_nonmem_model.Rmd'}
```

```{r child = './rmd/06_run_ctl/02_model_diagnostic.Rmd'}
```


```{r child = './rmd/07_run_cpp/01_run_sim.Rmd'}
```

```{r child = './rmd/08_exposure_response/01_exposure_response.Rmd'}
```

```{r child = './rmd/09_advanced_model/01_advanced_model.Rmd'}
```

```{r child = './rmd/10_reporting/01_reporting.Rmd'}
```

```{r child = './rmd/90_appendix/01_global_setting.Rmd'}
```

```{r child = './rmd/90_appendix/01_global_variable_notused.Rmd'}
```

```{r child = './rmd/90_appendix/01_model_library.Rmd'}
```

```{r child = './rmd/90_appendix/02_dplyr.Rmd'}
```

```{r child = './rmd/90_appendix/03_ggplot.Rmd'}
```

```{r child = './rmd/90_appendix/04_mrgsolve.Rmd'}
```

```{r child = './rmd/90_appendix/05_tools.Rmd'}
```
 

```{r child = './rmd/references.Rmd'}
```



```{r setup99, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.





## Introduction {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r pressureplot,  fig.cap='Inteactive histogram plot!'}
plotOutput("pressureplot")
```

 

```{r nice-fig, context="server", fig.cap='Here is a nice figure!', fig.align='center', tidy=FALSE}
output$pressureplot <- renderPlot({
 #out.width='80%', fig.asp=.75,
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
})

```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].   [@R-shiny].

## Shiny

Here is a review of existing methods.
 

```{r data, include=FALSE}
library(dplyr)
faithful_data <- sample_n(faithful, 100)
```
 

```{r}
selectInput("n_breaks", label = "Number of bins:",
            choices = c(10, 20, 35, 50), selected = 20)

sliderInput("bw_adjust", label = "Bandwidth adjustment:",
            min = 0.2, max = 2, value = 1, step = 0.2)
```
 

### Geyser Eruption Duration

```{r histogram_plot,  fig.cap='Inteactive histogram plot!'}
plotOutput("eruptions")
```

```{r, context="server"}
output$eruptions <- renderPlot({
  hist(faithful_data$eruptions, probability = TRUE,
       breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser Eruption Duration")

  dens <- density(faithful_data$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```


http://www.dartistics.com/rmarkdown-shiny.html
 see histogram plot Figure \@ref(fig:histogram_plot).
