 

# Simulation <a name="chapter_simulation"></a>

This chapter is dedicated for simulation and post-process of the simulated data. 
In particular, R package *mrgsolve* is used as the simulation engine. 
For more details on using *mrgsolve* see <https://mrgsolve.github.io/>.

1. For running simulations, see section [run simulation](#sec_run_sim); 
2. For post-processing simulated data, 
    + to derive exposure matrices, see section [summarise exposure metrices](#sec_summarise_exposure); 
    + to calculate percent of population above certain threshold, 
      see section [calculate pct threshold](#sec_pct_threshold); 
    + to plot VPC, see section [plot VPC](#sec_plot_VPC); 
  
 

## Run simulation <a name="sec_run_sim"></a>

To run simulation using R, you need to have a *mrgsolve* model specification file (called .cpp file). 
Typically, a simulation is based on the following scenario including 

1. population mean simulation for a typical subject (i.e. without inter-subject variability); 
2. population simulation (with inter-subject variability); 
3. post-hoc simulation for a given population with their corresponding post-hoc model parameters.

```{r}
output$run_simulation <- renderUI({ 
   
  ALL = callModule(module_runsim, "run_simulation", 
                   ALL, cppModel_name = "mYtEsT_for_run_simulation")  
  module_runsim_UI(id="run_simulation", label = NULL)

})

fluidRow(column(12, uiOutput("run_simulation")))
```

 
 
## Summarise exposure <a name="sec_summarise_exposure"></a>
In this section, you can calculate the individual exposure metrics 
based on the simulated data, and then summarise them, typically based on their dose groups, 
to generate a variety of summary tables and appropriate visualizations. 

```{r, eval=FALSE}
# #-----------------------------------------
# # data_selector
# #-----------------------------------------
# output$data_selector_for_summarise_exposure <- renderUI({
# 
#   validate(need(ALL$DATA, message=FALSE))
#   
#   data.lst = c("", unique(names(ALL$DATA)))
#   selectizeInput(("data_name_for_summarise_exposure"), 
#                  label    = "select dataset:" , 
#                  choices  = data.lst,  #unique(inputData()%>%pull(TEST)),    
#                  multiple = FALSE, 
#                  
#                  selected = data.lst[1])  #unique(inputData()%>%pull(TEST))[1])   
# })
#fluidRow(column(12, uiOutput(("data_selector_for_summarise_exposure"))))
  
```


```{r}
output$load_dataset_for_summarise_exposure_container <-renderUI({
  # callModule  
  ALL = callModule(module_load_dataset, "load_dataset_for_summarise_exposure", 
                     ALL, dataset_name="mYtEsT_for_summarise_exposure")

  # UI  
  fluidRow(column(6, 
                   module_load_dataset_UI(id="load_dataset_for_summarise_exposure", label=NULL)
                 ), 
           column(6, 
                   HTML(colFmt("internal library: build-in dataset <br>
                                within session: secondary data derived <br> 
                                external file: external file", color="gray")
                        )
                   )
           )  
  })
fluidRow(column(12, uiOutput(("load_dataset_for_summarise_exposure_container"))))
```
 
  
```{r} 
output$summarise_exposure<- renderUI({  
  validate(need(ALL$DATA[["mYtEsT_for_summarise_exposure"]], message=FALSE))
  
  #script = readLines(paste0(HOME, "/script/simdata_summary_exposure.R"))
  #script = paste0(script, collapse="\n")
  
  
  file_lst <- list.files(path=paste0(HOME, "/script/"), pattern="simdata_summary_exposure")
  script <- sapply(file_lst, function(i) paste0(readLines(paste0(HOME, "/script/", i)), collapse="\n") ) %>% unlist()

  ALL =  callModule(module_run_script, "summarise_exposure", ALL, 
                    dataset=ALL$DATA[["mYtEsT_for_summarise_exposure"]], 
                    script)

  module_run_script_UI(("summarise_exposure"), label = NULL) 
     
})

fluidRow(column(12, uiOutput("summarise_exposure")))
```
  


## Set threshold <a name="sec_pct_threshold"></a>
In this section, you may calculate the percent of population above a specified threshold concentration.  

 
```{r} 
output$load_dataset_for_pct_threshold_container <-renderUI({
  # callModule 
  ALL = callModule(module_load_dataset, "load_dataset_for_pct_threshold", 
                     ALL, dataset_name="mYtEsT_for_pct_threshold")
  
  # UI  
  fluidRow(column(6, 
                   module_load_dataset_UI(id="load_dataset_for_pct_threshold", label=NULL)
                 ), 
            column(6, 
                   HTML(colFmt("internal library: build-in dataset <br>
                                within session: secondary data derived <br> 
                                external file: external file", color="gray")
                        )
                   )
            )  
  })
fluidRow(column(12, uiOutput(("load_dataset_for_pct_threshold_container"))))
```


```{r}
output$pct_threshold<- renderUI({  
  validate(need(ALL$DATA[["mYtEsT_for_pct_threshold"]], message=FALSE))
  
  script = readLines(paste0(HOME, "/script/simdata_pct_threshold.R"))
  script = paste0(script, collapse="\n")

  ALL =  callModule(module_run_script, "pct_threshold", ALL, 
                    dataset = ALL$DATA[["mYtEsT_for_pct_threshold"]], 
                    script)

  module_run_script_UI(("pct_threshold"), label = NULL) 
})

fluidRow(column(12, uiOutput("pct_threshold")))
```
  

## Plot VPC <a name="sec_plot_VPC"></a>
In this section, you may overlay the observed data on top of simulation data with 95% CI. 

```{r, eval = FALSE}
#-----------------------------------------
# data_selector
#-----------------------------------------
tagList(
fluidRow(column(12, uiOutput(("simdata_selector_for_VPC")))),
  
fluidRow(column(12, uiOutput(("obsdata_selector_for_VPC"))))
)

output$simdata_selector_for_VPC <- renderUI({

  validate(need(ALL$DATA, message=FALSE))
  
  data.lst = c("", unique(names(ALL$DATA)))
  selectizeInput(("simdata_name_for_VPC"), 
                 label    = "select simulated dataset:" , 
                 choices  = data.lst,  #unique(inputData()%>%pull(TEST)),    
                 multiple = FALSE, 
                 
                 selected = data.lst[1])  #unique(inputData()%>%pull(TEST))[1])   
})

output$obsdata_selector_for_VPC <- renderUI({

  validate(need(ALL$DATA, message=FALSE))
  
  data.lst = c("", unique(names(ALL$DATA)))
  selectizeInput(("obsdata_name_for_VPC"), 
                 label    = "select observed dataset:" , 
                 choices  = data.lst,  #unique(inputData()%>%pull(TEST)),    
                 multiple = FALSE, 
                 
                 selected = data.lst[1])  #unique(inputData()%>%pull(TEST))[1])   
})

  

```
 
  


```{r} 
output$load_dataset_for_plot_VPC_container <-renderUI({
  # callModule 
  ALL = callModule(module_load_dataset, "load_dataset_for_plot_VPC", 
                     ALL, dataset_name="mYtEsT_for_plot_VPC")

  # UI  
  fluidRow(column(6, 
                   module_load_dataset_UI(id="load_dataset_for_plot_VPC", label=NULL)
                 ), 
            column(6, 
                   HTML(colFmt("internal library: build-in dataset <br>
                                within session: secondary data derived <br> 
                                external file: external file", color="gray")
                        )
                   )
            )  
  })
fluidRow(column(12, uiOutput("load_dataset_for_plot_VPC_container")))
```


```{r}
output$plot_VPC<- renderUI({  
  validate(need(ALL$DATA[["mYtEsT_for_plot_VPC"]], message=FALSE))
  
  script= readLines(paste0(HOME, "/script/simdata_plot_VPC.R"))
  script  = paste0(script, collapse="\n")

  ALL =  callModule(module_run_script, "plot_VPC", ALL, 
                    dataset=ALL$DATA[["mYtEsT_for_plot_VPC"]], 
                    script)

  module_run_script_UI(("plot_VPC"), label = NULL) 
})

fluidRow(column(12, uiOutput("plot_VPC")))
```
 
  
 
