
## Model diagnostic  <a name="model_diagnostic"></a>

This section is to perform any diagnostic analysis of a given nonmem run. 

TUTORIAL
Model Evaluation of Continuous Data Pharmacometric
Models: Metrics and Graphics

https://ascpt.onlinelibrary.wiley.com/doi/pdf/10.1002/psp4.12161

 
 Shiny applications for pharmacometrics
 https://rdrr.io/github/pnolain/popkinr/
  
  RichardHooijmaijers/shinyMixR: Shiny dashboard interface for nlmixr
 https://rdrr.io/github/RichardHooijmaijers/shinyMixR/src/R/gof_plot.r
 
 https://ascpt.onlinelibrary.wiley.com/doi/pdf/10.1002/psp4.12445
 Nonlinear Mixed-Effects Model Development and
Simulation Using nlmixr and Related R Open-Source
Packages




```{r}
user.name = tolower(Sys.info()["user"])  # determineCurrentUser()
values4xpdb = reactiveValues(diagnostic=NULL) 
```

 

 




```{r, eval=FALSE}
# read xpdb using xpose.data

 xpdb_inputData <- reactive({
   validate(need(input$which_program, message=FALSE), 
            need(input$which_runno, message=FALSE) 
   )  
 
  file.dir = paste0(HOME, "/output/", 
             user.name, "/", 
             input$which_program, "/ctl/", 
             input$which_runno, "/")
  text = "xpdb = xpose.data('001', directory = file.dir)"  # default all "001"
  
  #error_message <- try_eval(text = text)
  output =  tryCatch(eval(parse(text=text))  , 
                     error=function(e) {
                       return(NULL)
                     } #, finally = {
                     # eval(parse(text=txt)) %>% as.data.frame()
                     #}
  ) 
     
 # "default, "message", "warning", "error"
 if (is.null(output)) {
   showNotification(paste0("failed to read in xpose.data"), type="error")
   xpdb = NULL
 }else { 
   showNotification(paste0("xpose.data read sucessfully"), type="message")   
   xpdb
 }
  #slot(xpdb, "Data") =  slot(xpdb, "Data") %>%  mutate(WRES=1)
  
  #input$which_program = "TEST"
  # input$which_run = "control5_THEOPP"
  #user.name = tolower(Sys.info()["user"])  # determineCurrentUser()
   
  #slotNames(xpdb)
  # "Xvardef"       "Labels"   "Graph.prefs"   "Miss"   "Cat.levels"    "DV.Cat.levels" "Subset"        "Gam.prefs"     "Bootgam.prefs"
  #slotNames(slot(xpdb,"Prefs"))
  
  #slot(slot(xpdb,"Prefs"), "Xvardef")
  #names(slot(slot(xpdb,"Prefs"), "Xvardef"))
  
   #xpdb =  slot(xpose4.obj,"Data")
  # runno = slot(xpose4.obj,"Runno")

  xpdb 
})
 
```

 



### Predefined plots <a name="predefined_diagnostic_plot"></a>

This section is for predefined diagnostic plots. 
If no data is found in this subsection, You may haven't loaded the **xpdb** yet or the loading failed.
See section [model diagnostic](#model_diagnostic). 

1. GOF1: basic goodness of fit, including diagonal plot of PRED/IPRED vs DV in both linear and log scale; <br>
2. GOF2: CWRES residue-based diagnostic plots;  <br>
3. GOF3: representive individual time-profile, overlaid with PRED and IPRED. <br>
4. VPC: There two approaches to perform VPC <br>
    + using **mrgsolve** to run the simulation, then VPC, 
      see chapter [run simulation](#chapter_simulation);
    + use **NONMEM** to run the simulation, then VPC, 
      see chapter [model development](#chapter_model_development);
5. ETAvsCOV: check any trend of ETA vs covariate (COV); <br>
6. ETAvsETA:  <br>


```{r, eval=FALSE}
# once have xpdb, generate all pre-defined plots

observeEvent({xpdb_inputData()}, {
      
  xpdb = xpdb_inputData() 
  validate(need(xpdb, message=FALSE))
   
  if (1==2) { 
   # tried to merge wit user_specified_diagnostic_plot
      tdata = slot(xpdb, "Data")
      output = diagnostic_GOF1(xpdb)
  
  #values4xpdb$diagnostic$PRED_DVOR$
  #    figure[["PRED_DVOR_LN"]] = fig 
  # figure[["PRED_DVOR_LN"]]$data =  tdata
  # figure[["PRED_DVOR_LN"]]$dataset = slot(xpdb, "Data")  # or xpdb
  #   
  }
  
  # all diagnostic plots 
  values4xpdb = xpdb_diagnostic_GOF1(xpdb, values4xpdb)
   
  values4xpdb = xpdb_diagnostic_GOF2(xpdb, values4xpdb) 

  values4xpdb = xpdb_diagnostic_GOF3(
   xpdb, values4xpdb, n=25, ids=NA)
   
  values4xpdb = xpdb_diagnostic_ETAvsETA(
   xpdb, values4xpdb, eta_name_lst=paste("ETA", 1:3, sep=""))
  
  #$ranpar  "Xvardef"   Prefs
  eta_name_lst = slot(slot(xpdb,"Prefs"), "Xvardef")$ranpar 
  values4xpdb = xpdb_diagnostic_ETAvsCOV(
   xpdb, values4xpdb, 
   cov_name_lst=c("WGTBL" ), 
   eta_name_lst=c("ETA1", "ETA2", "ETA3" )
   )
 })


# now render all predefined diagnostic plots
ALL = callModule(module_model_diagnostic_predefined, "assess_model", 
                 ALL, 
                 xpdb = xpdb_inputData(), 
                 values4xpdb)

module_model_diagnostic_predefined_UI(("assess_model"), label = NULL)
     
```
 
 

### User-specified plots <a name="user_specified_diagnostic_plot"></a>

This section is for user-specified diagnostic plots. 
If no data was found in this subsection, You may haven't loaded the **xpdb** yet or the loading failed.
See section [model diagnostic](#model_diagnostic). 
  

```{r}  
 
output$user_specified_diagnostic_plot <- renderUI({ 
  
  #validate(need(xpdb_inputData(), message="no data found yet"))
   
  # script
  script <- list.files(path=paste0(HOME, "/script/"), 
                         full.names = TRUE,
                         pattern="user_specified_diagnostic_plot")
  names(script) = basename(script)
  
  # module_run_script
  ALL = callModule(module_run_xpdb, "user_specified_diagnostic_plot", 
                   ALL, 
                   dataset=xpdb_inputData(), 
                   dataset_name="", 
                   script=script, 
                    params=NULL)

  module_run_xpdb_UI(("user_specified_diagnostic_plot"), label = NULL) 
     
})

fluidRow(column(12, uiOutput(("user_specified_diagnostic_plot"))))

```
 
  


 
 
