
# Population and samples

This chapter is to summarise the input dataset in term of the samples, the patient demographic, 
laboratory information, and their corresponding statistics.  



```{r, summary_population_samples}
#----------------------------------------------------
# standardize_adex
#----------------------------------------------------

output$summary_population_samples <-renderUI({
  validate(need(globalVars$login$status, message=FALSE))
  
  script <- list.files(path=paste0(HOME, "/script/"), 
                         full.names = TRUE,
                         pattern="accouting")
  names(script) = basename(script)
  
  # callModule 
  ALL = callModule(module_run_script, "summary_population_samples", 
                   ALL, 
                   dataset_name="mYtEsT_for_summary_population_samples",
                   script=script,
                   params = NULL
  )
  
  # UI  
  fluidRow(column(12, 
                  module_run_script_UI(id="summary_population_samples", label=NULL)
                  ) 
  )  
})

fluidRow(column(12, uiOutput(("summary_population_samples"))))
```



## Population

to summarize the population for each analyte (concentration, target, biomarker, efficacy, etc)
 
```{r }

adpc <- read_datafile(paste0(HOME, "/data/adpc.csv"))
tabl <- summary_of_studies(adpc, 
                   group_by=c("STUDYID", "ARMA"), 
                   value="DVOR", 
                   id="USUBJID"
)

caption = 'Summary of Population Included in the Study'
knitr::kable(tabl, booktabs = TRUE, caption=caption)      #, padding = 2
   
```

## Samples

to summarize the sample accounting for each analyte (concentration, target, biomarker, efficacy, etc)


## Demographic and lab information  

to summarize demographic and lab information


 
 
```{r, eval=FALSE}
 
 
#----------------------------------------------------------------------------
# Version 0.1   Created on 11/08/2018, Feng Yang
# 
#----------------------------------------------------------------------------
# Input
# -----------------
# 1) nmdat:  meta data file, or 
#
# Output Tables: 
#------------------
# 1) Overall population and samples
#    a. overall accounting table for subject, 
#    b. overall accounting table for sample,
# 2) summary table for PK, target and PD response by ARMA
#    a. PK sample, and disposition table
#    b. Target/PD sample, and disposition table 
# 3) summary table for patient demographics
#----------------------------------------------------------------------------
# 
nmdat <- read_datafile(paste0(HOME, "/data/nmdatPKPD.csv"))
tabl <- summary_of_studies(nmdat, 
                           group_by=c("STUDYID", "ARMA"), 
                           value="DVOR", 
                           id="USUBJID"
)

TABLE = NULL
##########################################################################################
# Overall population and samples 
##########################################################################################


# make ARMA as a ordered factor

nmdat <- nmdat %>% convert_vars_type(nmdat_data_type)

nmdat = nmdat %>% 
  #filter(as_numeric(TIME)>=0) %>%    # Do we want to exclude all pre-dose sampels, as the default?
  filter(TEST!=".", !is.na(DVOR)) 


study_name = ifelse(
  !"STUDYID" %in% colnames(nmdat), "STUDYID",
  paste0(nmdat %>% drop_na(STUDYID) %>% pull(STUDYID) %>% unique(), collapse=", ")
)

drug_name = ifelse(
  !"EXTRT" %in% colnames(nmdat), "EXTRT",
  paste0(nmdat %>% drop_na(EXTRT) %>% pull(EXTRT) %>% unique(), collapse=", ")
)

test_name = ifelse(
  !"TESTCD" %in% colnames(nmdat), "TESTCD",
  paste0(nmdat %>% drop_na(TESTCD) %>% pull(TESTCD) %>% unique(), collapse=", ")
)

test_label = ifelse(
  !"TEST" %in% colnames(nmdat), "TEST",
  paste0(nmdat %>% drop_na(TEST) %>% pull(TEST) %>% unique(),  collapse=", ")
)


#----------------------------------------------------------------------------
# Table accounting_subject:  Accounting of All Subjects by Analyte, Treatment Group, and Overall  
#----------------------------------------------------------------------------

tabl = nmdat %>% group_by(TEST, ARMA) %>% summarise(N=length(unique(USUBJID)) ) %>% 
  spread(ARMA, N) %>% ungroup()

tabl = cbind(tabl,  Overall =  rowSums(tabl%>%select(-TEST)))
tabl


attr(tabl, 'title') <- paste0("Accounting of Subjects by Analyte, Treatment Group, and Overall (", study_name, ")") # 
TABLE[["accounting_subject"]]  = tabl 

#----------------------------------------------------------------------------
# Table accounting_sample: Accounting of All Samples by Analyte, Treatment Group, and Overall
#----------------------------------------------------------------------------
tabl = nmdat %>% group_by(TEST, ARMA) %>% summarise(N=length(DVOR) )    %>% 
  spread(ARMA, N) %>% ungroup()


t1 = nmdat %>% group_by(TEST) %>% summarise(N=length(DVOR), 
                                            Quantifiable.samples = length(which(DVOR!=0))) %>% 
  ungroup()


tabl = cbind(cbind(tabl,  TOTAL =  rowSums(tabl%>%select(-TEST))), Quantifiable=t1$Quantifiable.samples)
tabl = tabl %>% mutate(Quantifiable=paste0(Quantifiable, "(", u.signif(Quantifiable/TOTAL*100, digits=3), "%)"))
tabl


attr(tabl, 'title') <- paste0("Accounting of All Samples by Analyte, Treatment Group, and Overall (", study_name, ")") # 
TABLE[["accounting_sample"]]  = tabl 



##########################################################################################
# summary_of_studies
##########################################################################################

#----------------------------------------------------------------------------
# Table summary_of_studies
#----------------------------------------------------------------------------
#namedVec2df <- function(x) {setNames(data.frame(lapply(x, type.convert), stringsAsFactors=FALSE), names(x))}

summary_of_studies0 <- function(nmdat, group_by=c("STUDYID", "ARMA", "EXROUTE"), value="DVOR", id="USUBJID") {
  # Note:   == "0",  mean  BLQ
  #         == ".",  missing, not available.
  
  summ = nmdat %>% mutate(DVOR=as_numeric(DVOR)) %>% 
    group_by_(.dots = group_by) %>% dplyr::summarise(
      N = fun.uniqN(USUBJID), 
      N_mininum_one_measurable_sample = fun.uniqN(USUBJID[!is.na(DVOR) & DVOR!=0]),
      N_subject = paste0(N, "(", N_mininum_one_measurable_sample, ")"), 
      
      N_samples = length(DVOR),
      
      N_predose_samples = length(DVOR[TIME<0]), 
      pct_predose_samples = paste0(N_predose_samples, "(", u.signif(N_predose_samples/N_samples*100, digits=3),"%)"),
      
      N_measurable_samples = length(DVOR[!is.na(DVOR) & DVOR!=0]), 
      pct_measurable_samples = paste0(N_measurable_samples, "(", u.signif(N_measurable_samples/N_samples*100, digits=3),"%)"),
      
      N_postdose_BLQ_samples = length(DVOR[TIME>=0 & DVOR==0]),
      #N_postdose_samples = length(DVOR[TIME>=0]),
      pct_postdose_BLQ_samples = paste0(N_postdose_BLQ_samples, "(", u.signif(N_postdose_BLQ_samples/length(DVOR[TIME>=0])*100, digits=3), "%)")
    ) %>% select(group_by, N_subject, N_samples, pct_predose_samples, pct_measurable_samples, pct_postdose_BLQ_samples)
  
  colnames(summ) <- c(group_by,  
                      "Number of Subjects(*)",	 	
                      "Number of Samples",
                      "Number of Pre-dose Samples",
                      "Number of Post-dose Quantifiable Samples (%)",	
                      "Number of Post-dose BLQ Samples (%)" 
  )
  return(summ)
  #   
  #   footnote:
  #   PK = pharmacokinetic; BLQ = below the level of quantification; IV = intravenous; SC = subcutaneous
  #   a Percentages of BLQ samples were computed relative to the total (measurable  + BLQ) sums of PK samples
  
}

summary_of_studies <- function(tdata, group_by=c("STUDYID", "ARMA"), value="DVOR", id="USUBJID") {
  tabl_1 = summary_of_studies0(tdata, group_by=c("STUDYID", "ARMA"), value="DVOR", id="USUBJID") 
  tabl_2 = summary_of_studies0(tdata, group_by=NULL, value="DVOR", id="USUBJID") 
  tabl = setNames(merge_all(list(tabl_1, tabl_2)), colnames(tabl_1))  %>% arrange(STUDYID, ARMA)  
  tabl = tabl %>% mutate(STUDYID=as.character(STUDYID), ARMA=as.character(ARMA))
  tabl_summary_study = tabl
  
  tabl[nrow(tabl), c("STUDYID","ARMA")] = "Total"
  tabl[which(duplicated(tabl$STUDYID)), "STUDYID"] = ""
  tabl = tabl %>% rename(Study=STUDYID, Group=ARMA)
  tabl[is.na(tabl)] = ""  
  return(tabl)
}

#----------------------------------------------------------------------------
# Table summary_of_studies for pk
#----------------------------------------------------------------------------

tdata = nmdat  %>% filter(TESTCAT=="PK")  # , PCTEST=="REGN2810 Concentration") 
tabl = summary_of_studies(tdata, group_by=c("STUDYID", "ARMA"))
if (length(unique(tabl%>% filter(!Study %in% c("", "Total"))%>% pull(Study)))==1) {tabl = tabl %>% select(-Study)}
tabl

attr(tabl, 'title') <- paste0("Summary of Subjects and PK Samples by Study and Treatment Group (", study_name, ")")
TABLE[["summary_studies_PK"]] = tabl 

#knitr::kable(tabl, booktabs = TRUE, caption=caption, padding = 2)

tabl = nmdat  %>% mutate(CFLAG=ifelse(is.na(CFLAG), ".", CFLAG)) %>% 
  filter(as.integer(EVID)==0)   %>% 
  group_by(STUDYID, CFLAG, TEST) %>% 
  dplyr::summarise(n.subject=length(unique(USUBJID)), 
                  n.sample =length(DVOR), 
                  n.subject_n.sample = paste0(n.subject, "(", n.sample, ")"))  %>%
  select(-n.subject, -n.sample) %>%
  spread(TEST, n.subject_n.sample) %>% as.data.frame()

attr(tabl, 'title') <- paste0("Summary of Subjects and PK Samples by Study and Treatment Group (", study_name, ")")
TABLE[["disposition_tabl_PK"]] = tabl 
 



#----------------------------------------------------------------------------
# summary stats for the continuous variables
#----------------------------------------------------------------------------

summary_continuous_var <- function(nmdat, id="USUBJID", group_by="ARMA", 
                                   COV_NAME=c( "AGE", "WGTBL", "HGTBL", "BMIBL"), 
                                   STATS_NAME=c("N", "Mean_SD", "Median", "Range") ) {
  
  #nmdat = nmdat %>% mutate(GROUP=paste(one_of(group_by), "-"))
  stopifnot(length(group_by)==1)
  t0 = lapply(COV_NAME, function(value, nmdat, id, group_by  ) {
    calc_stats(nmdat, id, group_by, value) %>% 
      mutate(COV_NAME=value, 
             Mean=u.signif(Mean, digits=3)%>%as.character(), 
             SD = u.signif(SD, digits=3)%>%as.character(), 
             SE = u.signif(SE, digits=3)%>%as.character()) }, nmdat, id, group_by)  %>%  
    
    bind_rows() %>% 
    select(one_of(group_by), COV_NAME, one_of(STATS_NAME)) %>%   
    gather("STATS_NAME", "value", one_of(STATS_NAME))  %>% 
    spread_(group_by, "value" )
  
  # add the Overall column
  t1 = nmdat  %>% gather("COV_NAME", "COV_VALUE",  one_of(COV_NAME) ) %>% 
    calc_stats(id, group="COV_NAME", value="COV_VALUE") %>% 
    mutate(Mean=u.signif(Mean, digits=3), 
           SD = u.signif(SD, digits=3), 
           SE = u.signif(SE, digits=3)) %>%        
    select(COV_NAME, one_of(STATS_NAME)) %>%   
    gather("STATS_NAME", "Overall", one_of(STATS_NAME)) 
  #%>%
  #rename(ARMA = COV_NAME)
  
  # merge 
  tcon = t0 %>% left_join(t1, by=c("COV_NAME", "STATS_NAME"))
  
  tcon$COV_NAME = ordered(tcon$COV_NAME, levels=COV_NAME)
  tcon$STATS_NAME = ordered(tcon$STATS_NAME, levels=STATS_NAME)      
  
  tcon <- tcon %>% arrange(COV_NAME, STATS_NAME)
  return(tcon)
}


#----------------------------------------------------------------------------
# summary stats for the categorical variables
#----------------------------------------------------------------------------
summary_categorical_var <- function(tdata, id="USUBJID", group_by="ARMA", 
                                    COV_NAME=c( "SEX", "RACE", "ETHNIC"), 
                                    STATS_NAME=c("N_PCT") ) {
  
  calc_stats_cat <-  function(adsl, id="USUBJID", group_by="ARMA", value="SEX") {
    #adsl = adsl %>% rename_(USUBJID=id, ARMA=group_by, COV_VALUE=value)
    # adsl$USUBJID = adsl[, id]
    # adsl$ARMA = adsl[, group_by]               
    # adsl$COV_VALUE  = adsl[, value]
    
    t1 = adsl %>% group_by_(.dots = group_by) %>% dplyr::summarise(N_ALL=fun.uniqN(USUBJID))       
    t2 = adsl %>% group_by_(.dots = c(group_by, value)) %>%  dplyr::summarise(N=fun.uniqN(USUBJID)) %>%       
      left_join(t1, by=group_by) %>% 
      mutate(PCT = as.character(u.signif(N/N_ALL*100, digits=3)), 
             N_PCT = as.character(paste(N, "(", PCT, "%)", sep="")) 
      ) %>% rename_(COV_VALUE=value)
    t2 = as.data.frame(t2)     
    
    return(t2)
  }
  
  t0 = lapply(COV_NAME, function(value, tdata, id, group_by ) {
    calc_stats_cat(tdata, id, group_by, value )%>%mutate(COV_NAME=value, COV_VALUE=as.character(COV_VALUE))}, tdata, id, group_by)  %>% 
    bind_rows() %>% 
    select(one_of(group_by), one_of("COV_NAME", "COV_VALUE"),  one_of(STATS_NAME)) %>%   
    #gather("STATS_NAME", "value",   CAT, N_PCT)  %>%  
    spread_(group_by, "N_PCT")
  
  # add the Overall column   
  tdata = tdata %>% rename_(USUBJID=id) # $USUBJID = tdata[, id]       
  t1 = tdata %>% gather(COV_NAME, COV_VALUE, one_of(COV_NAME)) %>% group_by(COV_NAME, COV_VALUE) %>% summarise(Overall=as.character(fun.uniqN(USUBJID)))
  
  # merge
  tcat = t0 %>% left_join(t1, by=c("COV_NAME", "COV_VALUE"))
  
  return(tcat)
}


CON_COV_NAME=c( "AGE", "WGTBL", "HGTBL", "BMIBL") 
# "CREATBL",       "CRCLBL",        "ALTBL" ,        "ASTBL" ,        "BILIBL" ,      
#"ALBBL",         "IGGBL" ,        "LDHBL" ,        "ALPBL")
CAT_COV_NAME=c("SEX", "RACE", "ETHNIC")
STATS_NAME=c("N", "Mean", "SD", "SE", "Median_Range")


tdata = nmdat  %>% distinct(USUBJID, .keep_all=TRUE)
tdata = tdata %>% arrange(STUDYID, ARMA) %>% mutate(STUDYID_ARMA = STUDYID)   # paste(STUDYID, ARMA, sep="~"))
tdata = tdata %>% mutate(STUDYID_ARMA=ordered(STUDYID_ARMA, level=unique(STUDYID_ARMA)))

t1 = summary_continuous_var(tdata, id="USUBJID", group_by=c( "STUDYID_ARMA"), 
                            COV_NAME=CON_COV_NAME, 
                            STATS_NAME=STATS_NAME) %>% 
  rename(COV_VALUE=STATS_NAME)


t2 = summary_categorical_var(tdata, id="USUBJID", group_by="STUDYID_ARMA", 
                             COV_NAME=CAT_COV_NAME, 
                             STATS_NAME=c("N_PCT") )  %>% 
  mutate(COV_VALUE=as.character(COV_VALUE))

tabl = bind_rows(t1, t2) %>% as.data.frame()


tabl

tabl =  tabl %>% mutate(COV_NAME = str_replace_all(COV_NAME, 
                                                   c("AGE" = "Age\n(year)", 
                                                     "RACE"= "Race", 
                                                     "SEX"= "Sex", 
                                                     "ETHNIC"= "Ethnicity", 
                                                     "WGTBL"= "Weight\n(kg)", 
                                                     "HGTBL"= "Height\n(m)", 
                                                     "ALBBL"= "Albumin\n(g/L)", 
                                                     "BMIBL"= "BMI\n(kg/m2)", 
                                                     "CREATBL"= "Creatinine\n(umol/L)", 
                                                     "CRCLBL"= "Creatinine \nClearance (mL/min)",     
                                                     "ALTBL"= "ALT\n(IU/L)", 
                                                     "ASTBL"= "AST\n(IU/L)", 
                                                     "BILIBL"= "Bilirubin\n(umol/L)", 
                                                     "IGGBL"= "IGG\n(g/L)", 
                                                     "LDHBL"= "LDH\n(IU/L)", 
                                                     "ALPBL"= "ALP\n(IU/L)", 
                                                     
                                                     "C5BL"= "Baseline C5\n(mg/L)", 
                                                     "CH50HBL"="Baseline CH50\n(U/mL)"
                                                   )),
                        
                        COV_VALUE = str_replace_all(COV_VALUE, 
                                                    c("NOT HISPANIC OR LATINO"= "Not Hispanic/Latino", 
                                                      "HISPANIC OR LATINO"= "Hispanic/Latino",     
                                                      "NOT REPORTED"= "Not Reported", 
                                                      "WHITE"= "White", 
                                                      "ASIAN"= "Asian", 
                                                      "BLACK OR AFRICAN AMERICAN"= "Black", 
                                                      "OTHERS"= "Others", 
                                                      "OTHER"= "Other", 
                                                      "AMERICAN INDIAN OR ALASKA NATIVE"= "Alaska native/Indian", 
                                                      "Median_Range"= "Median(range)"
                                                    ))
                        
)




# Remove duplicates
tabl = tabl %>% 
  #group_by(PARAMS) %>%  
  mutate(COV_NAME=ifelse(duplicated(COV_NAME), "", COV_NAME)) 
#tabl$PARAMS[duplicated(tabl$PARAMS)] = ""

# extend colnames of tabl    
colnames(tabl) = colnames(tabl) %>% str_replace_all(
  c("PARAMS" = "Metrics",  
    "COV_NAME" = "Covariate",
    "COV_VALUE" = "Stats/Category",
    "Mean_SD"= "Mean(SD)" 
  ))




#tabl[which(duplicated(tabl$COV_NAME)), "COV_NAME"] = ""
tabl[is.na(tabl)] = ""
colnames(tabl) <- gsub("COV_NAME", "Covariate", colnames(tabl), fix=TRUE)
colnames(tabl) <- gsub("COV_VALUE", "Statistics", colnames(tabl), fix=TRUE)


attr(tabl, 'title') <- paste0("Summary of Baseline Demographic Characteristics, Laboratory and Disease Status Variables (", study_name, ")")
TABLE[["summary_demog"]] = tabl 

```
