
## Model-based check   <!-- {.tabset .tabset-pills}--> 

back to [nonmem_dataset_integrity_check](#nonmem_dataset_integrity_check)
 
```{r}
 
   nmdat_buildIn_model_check <- function(nmdat, cppModel, values4nmdat)  {
     validate(need(nmdat, message=FALSE), 
              need(cppModel, message=FALSE))
          
     values4nmdat = newuoa_parameter_estimation(nmdat, cppModel, values4nmdat)
       
     values4nmdat = newuoa_simulation(nmdat, cppModel, values4nmdat)
 
     values4nmdat = newuoa_diagnostic_PRED_DVOR(nmdat, cppModel, values4nmdat)
       
       
   return(values4nmdat)
   }
   
```


### Load model 


```{r}
renderUI({
  ALL = callModule(module_load_cppModel, "load_cppModel_for_integrity_check", ALL)
  
  module_load_cppModel_UI(id="load_cppModel_for_integrity_check", label="load_cppModel") 
  })
 
```

```{r}
cppModel_inputData <- reactive({
 
  validate(need(ALL$cppModel, message=FALSE))
  print("in cppModel_inputData  ")
 
  cppModel = ALL$cppModel[['cppModel_nmdat_check']] 
  cppModel
})
  
   
```





### Define objective function

```{r define_objective_function}
##' Function returning the objective function
ols <- function(mod, theta, nmdat, pred=FALSE) {
  
  # remove all non-numeric columns
  nmdat = nmdat %>% mutate(ARMA=as.character(ARMA))
  
  tdata = nmdat[, setdiff(colnames(nmdat), names(which(sapply(nmdat, class) == "character")))]
   
  theta <- setNames(lapply(theta, exp), names(theta))
  
  out<- 
    mod %>% 
    param(theta) %>%
    data_set(tdata) %>% 
    Req(CONC) %>% 
    drop.re %>%
    mrgsim(obsonly=TRUE, tad=TRUE, carry.out=c("DVOR", "EVID")) %>%
    filter(!is.na(CONC) & TIME!=0)
  
  out = out %>% left_join(nmdat %>% as.data.frame() %>% 
                            distinct(ID, .keep_all=TRUE) %>% 
                            select(ID, ARMA, USUBJID),
                          by=c("ID")) %>% 
    mutate(ARMA = ordered(ARMA, levels = unique(ARMA)))
  
  if(pred)  return(out)
  
  EPS = 1E-8
  log.yhat <- log(as.numeric(out$CONC + EPS))
  log.y    <- log(as.numeric(out$DVOR) + EPS)
  obj = sum((log.y - log.yhat)^2)
  #print(paste0("obj=", obj))
  
  return(obj)
}

```

### Parameter estimation

```{r model_parameter_estimation, include=FALSE, eval=TRUE}

newuoa_parameter_estimation <- function(nmdat, cppModel, values4nmdat)  {
    
  validate(need(nmdat, message=FALSE), 
          need(cppModel, message=FALSE)
  )
  
  print("loading..OK")
  print( cppModel   %>% param())
   
  ##' Initial estimates
  theta <- cppModel %>% param(TVCL=1.125676) %>% param()   %>% as.numeric()   # log(c(DENCL=6, DENVC=3000, DENVMAX=1000, DENVP=3000))
  
  param.lst = c("TVCL" , "TVV2",  "TVQ",   "TVV3",  "TVKA" ,  "TVF1", "TVVMAX","TVKSS" )
  theta = theta[param.lst]
  
  theta = theta %>% log()
  #theta
  
  
  
  
  # Fit with `minqa::newuoa`
  # ----------------------------
  #fit1 <- newuoa(theta=theta, fn=ols, d=d, n=names(theta), control=list(iprint=5))
  tdata <- nmdat %>% filter(TIME>=0, C!="C")
  
  fit1 <- newuoa(par=theta, fn=ols, mod=cppModel, nmdat=tdata, control=list(iprint=5))
  #exp(fit1$par)
  #as.numeric(param(mod))[names(theta)]
  
  est2 = fit1$par
  est2 <- setNames(est2, names(theta))
   
  values4nmdat$newuoa$params =  est2  
  
    print("done.  parameters found: ")
  print( est2)
  
  return(values4nmdat)
}

```

newly estimated parameters

```{r, tab.caption="newly estimated parameters", eval=TRUE}
# theta <- mod %>% param()   %>% as.numeric()   # log(c(DENCL=6, DENVC=3000, DENVMAX=1000, DENVP=3000))
# param.lst = c("TVCL" , "TVV2",  "TVQ",   "TVV3",  "TVKA" ,  "TVF1", "TVVMAX","TVKSS" )
# theta = theta[param.lst]

#renderUI({
 #   validate(need(values4nmdat$newuoa$params, message=FALSE) )
  
    renderPrint({  
      #print("values4nmdat$newuoa$params")
      #print(values4nmdat$newuoa$params)
      
      validate(need(values4nmdat$newuoa$params, message=FALSE))
      exp(values4nmdat$newuoa$params  )  
      
      })
  # callModule(default_tabOutput, "newuoa.params",  
  #              mytab = exp(values4nmdat$newuoa$params))
  # 
  # default_tabOutput_Input(id="newuoa.params", 
  #                         label="newuoa.params" ) 
#}) 
 

```



```{r}
  # We can run observers in here if we want to
  observe({
    msg <- sprintf("File %s was uploaded", values4nmdat$newuoa$params)
    cat(msg, "\n")
  })
```
   
  

### Run simulation

```{r}
# with updated parameters, re-run the model
# ----------------------------------------------

newuoa_simulation <- function(nmdat, cppModel, values4nmdat)  {
  validate(need(nmdat, message=FALSE), 
           need(cppModel, message=FALSE),
           need(values4nmdat$newuoa$params, message=FALSE)
  )
     print("simulation....     : ")
   
theta <- cppModel %>% param(values4nmdat$newuoa$params) %>% param()  %>% as.numeric()   # log(c(DENCL=6, DENVC=3000, DENVMAX=1000, DENVP=3000))
param.lst = c("TVCL" , "TVV2",  "TVQ",   "TVV3",  "TVKA" ,  "TVF1", "TVVMAX","TVKSS" )
theta = theta[param.lst] #%>% log()

tdata <- nmdat %>% filter(TIME>=0, C!="C" )
simData <- ols(cppModel, theta=theta,  tdata, pred=TRUE) %>% 
  mutate(PRED = CONC, 
         DV = DVOR, 
         WRES = (PRED-DV)^2#/DV^2
  )
 
values4nmdat$newuoa$simData =  simData 

fig = ggplot(simData, aes(x=TIME, y=PRED, group=USUBJID)) + 
  geom_point() + geom_line() +  
  geom_point(data=simData, aes(x=TIME, y=DVOR, group=USUBJID)) + 
  
  geom_point(data=simData%>%arrange(-WRES)%>%top_n(50), aes(x=TIME, y=DVOR, group=USUBJID), col="red") + 
  
  facet_wrap(~ARMA, scales="free") + 
  theme_bw() + base_theme(font.size = 12) + 
  xlab("Time(day)") + 
  ylab("Predicted/Observed Concentration (mg/L)")
  
values4nmdat$newuoa$timeProfile = fig

return(values4nmdat)
}
 
 renderUI({ 
    
    validate(need(values4nmdat$newuoa$timeProfile, message=FALSE), 
             need(values4nmdat$newuoa$simData, message=FALSE)
    )
    
    callModule(module_ggplot_brush, "ggplot.newuoa.timeProfile", 
              fig=  values4nmdat$newuoa$timeProfile , 
              mydata = values4nmdat$newuoa$simData, 
              xvar="TIME", yvar="PRED")
     
    module_ggplot_brush_UI(id="ggplot.newuoa.timeProfile", label = "ggplot.newuoa.timeProfile")
  
   })
   
```


### Diagnostic plot

```{r diagnostic_plot, anchor="figure", fig.cap="Diagnostic plot of PRED vs DV "}


newuoa_diagnostic_PRED_DVOR <- function(nmdat, cppModel, values4nmdat)  {
  # not used nmdat and cppModel
   
  validate(#need(nmdat, message=FALSE), 
           #need(cppModel, message=FALSE),
           need(values4nmdat$newuoa$simData, message=FALSE)
  )
  
  
  simData = values4nmdat$newuoa$simData 
  
limits = range(simData$DVOR, na.rm=TRUE)

#population prediction PRED
p1 <- ggplot(data=simData, aes(x=PRED,y=DVOR, col=ARMA)) +
  ggtitle("Observed vs Predited (Linear)")+
  xlab("Population Predictions") + ylab("Observed") +
  geom_point()+   
  
  geom_point(data=simData%>%arrange(-WRES)%>%top_n(50), aes(x=PRED, y=DVOR), col="red") + 
  
  coord_fixed(ratio=1, xlim = limits, ylim = limits) +   
  #geom_smooth(show.legend = FALSE,lwd=1,alpha=0.5)+ 
  geom_abline(show.legend = FALSE,intercept=0,slope=1)+
  theme_bw() +  base_theme(font.size = 12)  + 
  guides(col=guide_legend(ncol=4,byrow=TRUE)) 
#theme(legend.position="none") 

tdata = simData %>% filter(!is.na(as_numeric(DVOR)), !is.na(as_numeric(PRED)))
limits = ifelse(limits<0.078, 0.039, limits)
p2 <- ggplot(data=tdata, aes(x=(PRED),y=(DVOR), col=ARMA)) +     #log(x$PRED[x$MDV==0]),log(x$DV[x$MDV==0]),xlab="Population Predictions (log)",ylab="Observed (log)",alpha=0.5)+
  ggtitle("Observed vs Predited (Log)")+
  xlab("Population Predictions (log)") + ylab("Observed (log)") +
  geom_point()+ 
  
  geom_point(data=tdata%>%arrange(-WRES)%>%top_n(50), aes(x=(PRED), y=(DVOR)), col="red") + 
  
  scale_x_log10(breaks = 10^(seq(-1,3,by=1)),      #trans_breaks("log10", function(x) 10^x),
                labels = 10^(seq(-1,3,by=1))) +      # trans_format("log10", math_format(10^.x))) +
  
  scale_y_log10(breaks = 10^(seq(-1,3,by=1)),      #trans_breaks("log10", function(x) 10^x),
                labels = 10^(seq(-1,3,by=1))) +      # trans_format("log10", math_format(10^.x))) +
  
  annotation_logticks(sides ="l") + 
  
  coord_fixed(ratio=1, xlim = (limits), ylim = (limits)) +       
  #geom_smooth(lwd=1,alpha=0.5)+ 
  geom_abline(intercept=0,slope=1)+
  theme_bw() +  base_theme(font.size = 12)  + 
  guides(col=guide_legend(ncol=4,byrow=TRUE))  

fig = p1 # multiplot(p1,p2,cols=2)

#fig <- recordPlot()
attr(fig, 'title') <- "Predicted vs Observed Concentration in Linear/Log Scale" 
attr(fig, 'width') <- 8
attr(fig, 'height') <- 8
#FIGURE_ALL[["PK_GOF1"]] = fig 

values4nmdat$newuoa$diagnostic_PRED_DVOR = fig

return(values4nmdat)
}


# 
# 
#  
  renderUI({ 
    validate(need(values4nmdat$newuoa$diagnostic_PRED_DVOR, message=FALSE), 
             need(values4nmdat$newuoa$simData, message=FALSE)
    )
    
    callModule(module_ggplot_brush, "ggplot.newuoa.diagnostic.PRED.DVOR", 
             fig=values4nmdat$newuoa$diagnostic_PRED_DVOR, 
             mydata = values4nmdat$newuoa$simData, 
             xvar="PRED", yvar="DV")
    
    module_ggplot_brush_UI(id="ggplot.newuoa.diagnostic.PRED.DVOR", 
                       label = "ggplot.newuoa.diagnostic.PRED.DVOR")
 
  })
   
   
```





```{r}
 observeEvent({ nmdat_inputData()}, {
                
   nmdat =nmdat_inputData()
   validate(need(nmdat, message=FALSE)
   )
   
   # all mandatory_check
   values4nmdat = nmdat_mandatory_check(nmdat, values4nmdat)  
  
   # all quick_check
   values4nmdat = nmdat_quick_check(nmdat, values4nmdat) 
   
   # all advanced check
   values4nmdat = nmdat_advanced_check(nmdat, values4nmdat) 
      
 })


```



```{r}
#nmdat_inputData()

 observeEvent({nmdat_inputData()}, {
                
   nmdat =nmdat_inputData()
   cppModel = cppModel_inputData() 
   
   validate(need(nmdat, message=FALSE), 
            need(cppModel, message=FALSE)
   )
    
   # all newuoa model 
   values4nmdat = nmdat_buildIn_model_check(nmdat, cppModel, values4nmdat) 
      
 })

```








```{r}
# http://pages.ucsd.edu/~tfeenstr/research/RMarkdownIntro.Rmd

# Tables are also a useful way to show your results. There are some awesome R packages that help create pretty tables for you: stargazer and xtable. If you don't have these packages installed, you should install them by running the following R code: 
# 
# install.packages("stargazer") 
# 
# install.packages("xtable")
# 
# If you already have them installed, you'll just need to load them, which I've already done in our first code chunk up at the top. 
# 
# ## Tables with xtable
# 
# ```{r partyid_gender, echo=FALSE, eval=TRUE, results="asis"}
# # Here I'm going to make a cross-tab table that shows the relationship between gender and party ID
# # Each row will be a party ID (strong democrat to strong republican)
# # Each column will be a gender (male, female)
# # I want to know what percentage of men are strong democrats, what percentage of women are strong democrats, etc. So, each column will sum to 100%
# 
# partyid_gender <- prop.table(table(d$V36, d$V1)[2:8,2:3], 2)
# 
# # Now I want to set it up to be pretty in the report
# 
# options(xtable.comment=FALSE)
# print(xtable(partyid_gender, type="latex", caption="Party ID by Gender"), caption.placement="top")
# 
# # In the code above, we've first told R to suppress a comment that otherwise appears above the latex table
# # Then we're telling it to print a table that we create with the xtable package. The table is what we stored our table as before (partyid_gender). 
# # type="latex" says that we want to use latex code for our formatting to generate the pretty table
# # caption="..." tells us what we want our caption to be
# # caption.placement="top" tells us that we want the caption on top of the table instead of underneath it
```










