
# Appendix {-}
 

## Global setting

This chapter is for a model library, in particular how to add, delete or retrieve a given model(s). 
All modles will be included, with their meta information, i.e. who developed it (author), when developed (year), 
key features of model (1/2 comparment, linear/nonlinear), which therapeutic area (area), which program, which study, etc.



### Standard naming convention  <a name="global_setting_standard_naming_convention"></a>

Standard naming convention for adsl, adex, adpc, and nmdat. 

```{r, eval=TRUE } 
 
table = NULL
file_name <- paste0(HOME, "/lib/pkmeta.xlsx")
  
# adsl
tabl = read_excel(file_name,sheet="adsl",col_names = TRUE)  %>% 
  as.data.frame() %>% filter(!is.na(standard.name)) %>% select(-which.column)
attr(tabl, "title") = "List of standard varaibles for adsl" 
attr(tabl, "footnote") = paste0("Note, variable labeled as tier=1 are key variables, tier=2 are secondary variables, tier=3 are optional variables.")
table[["adsl"]] = tabl

# adex
tabl = read_excel(file_name,sheet="adex",col_names = TRUE)  %>% 
  as.data.frame() %>% filter(!is.na(standard.name)) %>% select(-which.column)
attr(tabl, "title") = "List of standard varaibles for adex" 
attr(tabl, "footnote") = paste0("Note, variable labeled as tier=1 are key variables, tier=2 are secondary variables, tier=3 are optional variables.")
table[["adex"]] = tabl 

# adpc
tabl = read_excel(file_name,sheet="adpc",col_names = TRUE)  %>% 
  as.data.frame() %>% filter(!is.na(standard.name)) %>% select(-which.column)
attr(tabl, "title") = "List of standard varaibles for adpc" 
attr(tabl, "footnote") = paste0("Note, variable labeled as tier=1 are key variables, tier=2 are secondary variables, tier=3 are optional variables.")
table[["adpc"]] = tabl 

# nmdat
tabl = read_excel(file_name,sheet="nmdat",col_names = TRUE)  %>% 
  as.data.frame() %>% filter(!is.na(standard.name)) %>% select(-which.column)
attr(tabl, "title") = "List of standard varaibles for nonmem dataset(nmdat)" 
attr(tabl, "footnote") = paste0("Note, variable labeled as tier=1 are key variables, tier=2 are secondary variables, tier=3 are optional variables.")
table[["nmdat"]] = tabl 
  
values = reactiveValues(figure=NULL, table=NULL, data=NULL)
values$table = table

################################
# checkInRows_container
 #fluidRow(column(12, uiOutput(("standard_dataset_container")))) 
 
################################
tabBox(width=12, id = ("standard_dataset"), title =NULL, 
       
        # adsl_container 
        tabPanel(width=12, title="adsl", value = "adsl", collapsible = TRUE, 
                 collapsed = TRUE, solidHeader = TRUE,
                 fluidRow(column(12, uiOutput(("adsl_container")))) 
        ),
       
       # adex_container 
       tabPanel(width=12, title="adex", value = "adex", collapsible = TRUE, 
                collapsed = TRUE, solidHeader = TRUE,
                  fluidRow(column(12, uiOutput(("adex_container")))) 
       ),        
       
       # adpc_container 
       tabPanel(width=12, title="adpc", value = "adpc", collapsible = TRUE, 
                collapsed = TRUE, solidHeader = TRUE,
                  fluidRow(column(12, uiOutput(("adpc_container"))))  
       ),     
           
       # nmdat_container
       tabPanel(width=12, title="nmdat", value = "nmdat", collapsible = TRUE, 
                collapsed = TRUE, solidHeader = TRUE,
                fluidRow(column(width=12, uiOutput(("nmdat_container"))))
       ) 
    ) # tabBox


output$adsl_container <- renderUI({  
  validate(need(is.list(values$table), message="No table found, or values$table needs to be a list"), 
           need(values$table[["adsl"]], message="no table found"), 
           need(is.data.frame(values$table[["adsl"]]), message="only data.frame allowed")
      )
    
  # module
   callModule(module_checkInRows, paste0("module_adsl_table"),  
                      values0 = values,
                      table_index = 1
  )   
  
  # UI
  module_checkInRows_UI((paste0("module_adsl_table")), label = NULL) 
 
})
   
output$adex_container <- renderUI({  
  validate(need(is.list(values$table), message="No table found, or values$table needs to be a list"), 
           need(values$table[["adex"]], message="no table found"), 
           need(is.data.frame(values$table[["adex"]]), message="only data.frame allowed")
      )
    
  # module
   callModule(module_checkInRows, paste0("module_adex_table"),  
                      values0 = values,
                      table_index = 2
  )   
  
  # UI
  module_checkInRows_UI((paste0("module_adex_table")), label = NULL) 
 
})
 
 
output$adpc_container <- renderUI({  
  validate(need(is.list(values$table), message="No table found, or values$table needs to be a list"), 
           need(values$table[["adpc"]], message="no table found"), 
           need(is.data.frame(values$table[["adpc"]]), message="only data.frame allowed")
      )
    
  # module
   callModule(module_checkInRows, paste0("module_adpc_table"),  
                      values0 = values,
                      table_index = 3
  )   
  
  # UI
  module_checkInRows_UI((paste0("module_adpc_table")), label = NULL) 
 
})

output$nmdat_container <- renderUI({  
  validate(need(is.list(values$table), message="No table found, or values$table needs to be a list"), 
           need(values$table[["nmdat"]], message="no table found"), 
           need(is.data.frame(values$table[["nmdat"]]), message="only data.frame allowed")
      )
    
  # module
   callModule(module_checkInRows, paste0("module_nmdat_table"),  
                      values0 = values,
                      table_index = 4
  )   
  
  # UI
  module_checkInRows_UI((paste0("module_nmdat_table")), label = NULL) 
 
})


```


### Naming convention

List of naming conventions and parameters for this handbook

```{r }
table = NULL
 # naming convention and parameters for this handbook 
file_name <- paste0(HOME, "/lib/pkmeta.xlsx")

convention_all_table =  read_excel(file_name,sheet="convention",col_names = TRUE)  %>% 
  as.data.frame() %>% filter(!is.na(domain))

# DATA
tabl <- convention_all_table %>% filter(domain=="DATA") %>% select(-domain)
attr(tabl, "title") = "List of naming conventions for data variables " 
attr(tabl, "footnote") = ""
table[["DATA"]] = tabl 

# SIMULATION
tabl <- convention_all_table %>% filter(domain=="SIMULATION") %>% select(-domain)
attr(tabl, "title") = "List of default parameters for simulation " 
attr(tabl, "footnote") = ""
table[["SIMULATION"]] = tabl 
 
# RUN_NONMEM
tabl <- convention_all_table %>% filter(domain=="NONMEM") %>% select(-domain)
attr(tabl, "title") = "List of default parameters for running nonmem jobs " 
attr(tabl, "footnote") = ""
table[["NONMEM"]] = tabl 

# GGPLOT
tabl <- convention_all_table %>% filter(domain=="GGPLOT") %>% select(-domain)
attr(tabl, "title") = "List of default parameters for ggplot visualization " 
attr(tabl, "footnote") = ""
table[["GGPLOT"]] = tabl 


values2 = reactiveValues(figure=NULL, table=NULL, data=NULL)
values2$table = table
 


################################
tabBox(width=12, id = ("naming_convention_params_app"), title =NULL, 
       
        # adsl_container 
        tabPanel(width=12, title="data", value = "data", collapsible = TRUE, 
                 collapsed = TRUE, solidHeader = TRUE,
                 fluidRow(column(12, uiOutput(("global_params_data_container")))) 
        ),
       
       # adex_container 
       tabPanel(width=12, title="simulation", value = "simulation", collapsible = TRUE, 
                collapsed = TRUE, solidHeader = TRUE,
                  fluidRow(column(12, uiOutput(("global_params_simulation_container")))) 
       ),        
       
       # adpc_container 
       tabPanel(width=12, title="NONMEM", value = "NONMEM", collapsible = TRUE, 
                collapsed = TRUE, solidHeader = TRUE,
                  fluidRow(column(12, uiOutput(("global_params_nonmem_container"))))  
       ),     
           
       # nmdat_container
       tabPanel(width=12, title="ggplot", value = "ggplot", collapsible = TRUE, 
                collapsed = TRUE, solidHeader = TRUE,
                fluidRow(column(width=12, uiOutput(("global_params_ggplot_container"))))
       ) 
 ) # tabBox


output$global_params_data_container <- renderUI({  
  validate(need(is.list(values2$table), message="No table found, or values$table needs to be a list"), 
           need(values2$table[["DATA"]], message="no table found"), 
           need(is.data.frame(values2$table[["DATA"]]), message="only data.frame allowed")
      )
    
  # module
   callModule(module_checkInRows, paste0("global_params_data"),  
                      values0 = values2,
                      table_index = 1
  )   
  
  # UI
  module_checkInRows_UI((paste0("global_params_data")), label = NULL) 
 
})
   
output$global_params_simulation_container <- renderUI({  
  validate(need(is.list(values2$table), message="No table found, or values$table needs to be a list"), 
           need(values2$table[["SIMULATION"]], message="no table found"), 
           need(is.data.frame(values2$table[["SIMULATION"]]), message="only data.frame allowed")
      )
    
  # module
   callModule(module_checkInRows, paste0("global_params_simulation"),  
                      values0 = values2,
                      table_index = 2
  )   
  
  # UI
  module_checkInRows_UI((paste0("global_params_simulation")), label = NULL) 
 
})

output$global_params_nonmem_container <- renderUI({  
  validate(need(is.list(values2$table), message="No table found, or values$table needs to be a list"), 
           need(values2$table[["NONMEM"]], message="no table found"), 
           need(is.data.frame(values2$table[["NONMEM"]]), message="only data.frame allowed")
      )
    
  # module
   callModule(module_checkInRows, paste0("global_params_nonmem"),  
                      values0 = values2,
                      table_index = 3
  )   
  
  # UI
  module_checkInRows_UI((paste0("global_params_nonmem")), label = NULL) 
 
})

output$global_params_ggplot_container <- renderUI({  
  validate(need(is.list(values2$table), message="No table found, or values$table needs to be a list"), 
           need(values2$table[["GGPLOT"]], message="no table found"), 
           need(is.data.frame(values2$table[["GGPLOT"]]), message="only data.frame allowed")
      )
    
  # module
   callModule(module_checkInRows, paste0("global_params_ggplot"),  
                      values0 = values2,
                      table_index = 4
  )   
  
  # UI
  module_checkInRows_UI((paste0("global_params_ggplot")), label = NULL) 
 
})


```
