 
```{r, eval=FALSE} 
  # Analysis Data Model (ADaM) datasets are much more flexible than SDTM (Study Data ... The structure of subject-level analysis dataset (ADSL) contains one record per subject .... ADPC (PK Concentrations Analysis Dataset) .... The most common OCCDS datasets are ADAE, ADCM, ADMH, ADEX, ADCE, and ADDS. Most of ...
  # https://www.quanticate.com/blog/adam-datasets-for-pharmacokinetic-pk-analysis
  
```

# Construct dataset <a name="construct_dataset"></a>

Having a standardized dataset is the key to use this handbook. Without it, you may experience more bugs or instabilities. Two approaches to construct a dataset were presented in this handbook,     

1. construct a preliminary nonmem dataset from scratch, i.e. from patient demographic information (`adsl`), dosing record information (`adex`), concentration information (`adpc`), etc. see section [Assemble nmdat](#assemble_nmdat); 
    + standardize patient demographic information, see section [adsl](#standardize_adsl); 
    + standardize dosing record information, see section [adex](#standardize_adex); 
    + standardize concentration information, see section [adpc](#standardize_adpc); 
    + standardize biomarker, efficacy end points, safety, etc, see section [other](#standardize_other); 
    + merge all these datasets,  see section [assemble](#merge_all); 
    
2. standardize a preliminary nonmem dataset, see section [Standardize nmdat](#standardize_nmdat); 

The goal of this data construction is to generate a master dataset containing PK, PD, biomarkers, doising records as well as demographic information, for subsequent pharmacokinetic analyses (either descriptive or modeling-based analysis). 
  
  
## Assemble nmdat <a name="assemble_nmdat"></a>

This section is to standardize the dataset for patient demographic information (*adsl*), dosing record information (*adex*), concentration information (*adpc*), followed by merging all to generate a nonmem-ready dataset. 
   
   
### adsl  <a name="standardize_adsl"></a>

First of all, let's standardize patient demographic information (*adsl*). 
The step-by-step instructions are following: 

1. Load the dataset (*adsl*), there are three ways to load: 

    + internal library: build-in dataset that this app can directly get access via computer physical drive; 
    + within session: saved data within session via computer cache memory;
    + external file: external files uploaded by users
    
    Once loaded, the dataset will be rendered in the tab of **dataset** in the following tabbox. 
    You may get familiar with this dataset
    by interactively using *search*, *slidebar*, *select page length*, *select columns*, *previous* and *next* page, etc.
  
    You may assign a name for this dataset and save it into the computer memory that can be retrieved later 
    (i.e. *within session*), or you may download it as ".csv" file.  

2. Tell which is which (**alignCols** tab), i.e. align the variables in your dataset to the ones expected in this app. 
  For example, subject identifier can be *ID*, *SUBJECT*, *SUBJID*, *CLID*, etc. However, this app
  use *USUBJID* as the only unique subject identifier. You need to tell which variable in your dataset
  corresponds to *USUBJID* by double clicking the question mark (?) in the table below. Once align them to 
  your best of knowledge, you may click *checkIn*.  Here are a few additional notes: 

    + *tier* indicate the level of importance of each variable. By default, study identifier (*STUDYID*), 
      unique subject identifier (*USUBJID*), and 
      baseline body weight (*WGTBL*) are the key (minimum) variables in the dataset of *adsl*. 
      If any one of these key variables missing in the datset, 
      they will be highlighted as "red". Those secondard (tier 2) variables, if missing, 
      will be highlighted as "yellow". You may still move ahead without any corrections. 
      The one highlighted as "blue" are optional variables (tier 3)  that are missing. 
      
    + *which.column* auto populate the variable names from your loaded dataset. 
      If matches found, they will be aligned in a row-wise manner. Otherwise, a question mark (?) will be displayed.
      
    + *type*: variable type (char, num, int, etc). 
      If alignments found, they will be forced to convert to the desired format for subseqent analyses.
      
    + The table shown below are similar as Excel worksheet, you may right click to 
      insert row, remove row, or alignment the cells, though it is generally not recommendated.
      
    + you may create your own standard format of *adsl* in the global setting at [Appendix](#global_setting_standard_naming_convention).
 

3. In the tab of **runScript**, click *run script* button if you accept the default scripting. 
It basically have two components: 

    + standardize the dataset, each variable one by one, 
    + report any abnormal scenario found in the checking process and the results 
    will be rendered in the next tab **curation**, 
  
    If you want to customize the default scripts, please follow the instruction within the scripts carefully. 
    Certain key words should not be changed; certain formatting should be followed. 
    
4. In the tab of **curation**, you will find a set of tables reporting any abnormality that
needs your manual curation. For examples, any subject whose baseline body weight is missing, or 
using non-standard naming convention for the variable of *SEX*. In default, this app uses 
*FEMALE*, *MALE*, and *UNKNOWN* as the standard ones. Once a table curated, click *confirm*. 
Once all tables curated, click *Save all*.  Please note:

    + the row(s) that are highlighted in the table, are the ones that can't be interpretable 
    and need your manual curation.
     
5. In the tab of **output**, a curated dataset is presented.  

    + You may assign a new name for this curated dataset and save it into the *session*. 
     
    
    
    

```{r, standardize_adsl}
#----------------------------------------------------
# standardize_adsl
#----------------------------------------------------
default_adsl_checkin <- reactive({ 
  read_excel(paste0(HOME, "/lib/pkmeta.xlsx"),sheet="adsl",col_names = TRUE)  %>% 
    as.data.frame() %>% filter(!is.na(standard.name))
})

output$standardize_adsl <-renderUI({
  validate(need(globalVars$login$status, message=FALSE))
  # 
  # script = readLines(paste0(HOME, "/script/build_adsl.R")) 
  # script = paste0(script, collapse="\n")
  
  script <- list.files(path=paste0(HOME, "/script/"), 
                         full.names = TRUE,
                         pattern="build_adsl")
  names(script) = basename(script)
  
  # callModule 
  # ALL = callModule(module_build_dataset, "standardize_adsl", 
  #                  ALL, 
  #                  dataset_name="mYtEsT_for_standardize_adsl",
  #                  script=script,
  #                  default_checkin = default_adsl_checkin()
  # )
  # 
  # # UI  
  # fluidRow(column(12, 
  #                 module_build_dataset_UI(id="standardize_adsl", label=NULL)
  #                 ) 
  # )
  
  callModule(module_build_dataset, "standardize_adsl",  
             ALL, 
             dataset_name="mYtEsT_for_standardize_adsl",   
             script = script,   
             params = NULL, 
             default_checkin = default_adsl_checkin()  
  ) 
  
  fluidRow(
    column(12, 
           module_build_dataset_UI(("standardize_adsl"), label = NULL)
    )
  )
  
  
})

tagList(
  fluidRow(column(width=12, tags$hr(style="border-color: gray;"))),
  fluidRow(column(12, uiOutput(("standardize_adsl"))))
)

```



### adex  <a name="standardize_adex"></a>

Here we standardize patient dosing records information (*adex*). 
By default, other than study identifier (*STUDYID*), unique subject identifier (*USUBJID*), 
these are the key variables of *adex*, including 
drug administration start date and time (*EXSTDTC*), 
drug administration end date and time (*EXENDTC*),
dose amount (*EXDOSE*),
dose unit, (*EXDOSU*), and 
route of administration (*EXROUTE*).
It is assumed that there is one single drug administered; otherwise,
actual treatment drug (*EXTRT*) must be included.

For general step-by-step instruction, 
please refer to section [adsl](#standardize_adsl). 


```{r, standardize_adex}
#----------------------------------------------------
# standardize_adex
#----------------------------------------------------
default_adex_checkin <- reactive({ 
  read_excel(paste0(HOME, "/lib/pkmeta.xlsx"),sheet="adex",col_names = TRUE)  %>% 
    as.data.frame() %>% filter(!is.na(standard.name))
})

output$standardize_adex <-renderUI({
  validate(need(globalVars$login$status, message=FALSE))
  
  script <- list.files(path=paste0(HOME, "/script/"), 
                         full.names = TRUE,
                         pattern="build_adex")
  names(script) = basename(script)
  
  # callModule 
  ALL = callModule(module_build_dataset, "standardize_adex", 
                   ALL, 
                   dataset_name="mYtEsT_for_standardize_adex",
                   script=script,
                   default_checkin =  default_adex_checkin()
  )
  
  # UI  
  fluidRow(column(12, 
                  module_build_dataset_UI(id="standardize_adex", label=NULL)
                  ) 
  )  
})

fluidRow(column(12, uiOutput(("standardize_adex"))))
```

### adpc  <a name="standardize_adpc"></a>

Here we standardize drug concentration information (*adpc*). 
By default, other than study identifier (*STUDYID*), unique subject identifier (*USUBJID*), 
these are the key variables of *adpc*, including 
sample collection date and time (*SAMDTTM*), and
dependent variable in the original format (*DVOR*). 

Many other variables such as unit of measurement (*DVOR*), their visit information (*VISIT*), 
Lower Limit of Quantitation (*LLOQ*), and Method of Test or Examination (*METHOD*), etc, need 
to be included to better interpret the dataset. 

For general step-by-step instruction, 
please refer to section [adsl](#standardize_adsl). 

```{r, standardize_adpc}
#----------------------------------------------------
# standardize_adpc
#----------------------------------------------------
default_adpc_checkin <- reactive({ 
  read_excel(paste0(HOME, "/lib/pkmeta.xlsx"),sheet="adpc",col_names = TRUE)  %>% 
    as.data.frame() %>% filter(!is.na(standard.name))
})

output$standardize_adpc <-renderUI({
  validate(need(globalVars$login$status, message=FALSE))
  
  script <- list.files(path=paste0(HOME, "/script/"), 
                         full.names = TRUE,
                         pattern="build_adpc")
  names(script) = basename(script)
    
  # callModule 
  ALL = callModule(module_build_dataset, "standardize_adpc", 
                   ALL, 
                   dataset_name="mYtEsT_for_standardize_adpc",
                   script=script,
                   default_checkin =  default_adpc_checkin()
  )
  
  
  # UI  
  fluidRow(column(12, 
                  module_build_dataset_UI(id="standardize_adpc", label=NULL)
                  ) 
          )  
})

fluidRow(column(12, uiOutput(("standardize_adpc"))))
```

### other  <a name="standardize_other"></a>

All other information, such as target, biomarker, and response are standardized 
in this subsection. Essentially, it is the same procedures as *adpc*.
By default, other than study identifier (*STUDYID*), unique subject identifier (*USUBJID*), 
these are the key variables of *other*, including 
sample collection date and time (*SAMDTTM*), and
dependent variable in the original format (*DVOR*). 

Many other variables such as unit of measurement (*DVOR*), 
analyte information (*TEST*), 
their corresponding visit information (*VISIT*), 
Lower Limit of Quantitation (*LLOQ*), and 
Method of Test or Examination (*METHOD*), etc, need 
to be included to better interpret the dataset. 


For general step-by-step instruction, 
please refer to section [adsl](#standardize_adsl). 

```{r, standardize_adpd}
#----------------------------------------------------
# standardize_adpd
#----------------------------------------------------
default_adpd_checkin <- reactive({ 
  read_excel(paste0(HOME, "/lib/pkmeta.xlsx"),sheet="adpc",col_names = TRUE)  %>% 
    as.data.frame() %>% filter(!is.na(standard.name))
})

output$standardize_adpd <-renderUI({
  validate(need(globalVars$login$status, message=FALSE))
  
  script <- list.files(path=paste0(HOME, "/script/"), 
                         full.names = TRUE,
                         pattern="build_adpc")
  names(script) = basename(script)
  
  # callModule 
  ALL = callModule(module_build_dataset, "standardize_adpd", 
                   ALL, 
                   dataset_name="mYtEsT_for_standardize_adpd",
                   script=script,
                   default_checkin =  default_adpd_checkin()
  )
  
  
  # UI  
  fluidRow(column(12, 
                  module_build_dataset_UI(id="standardize_adpd", label=NULL)
                  ) 
          )  
})

fluidRow(column(12, uiOutput(("standardize_adpd"))))
```

### merge  <a name="merge_all"></a>
 
This subsection is to merge all datasets previously standardized, to generate a nonmem-ready dataset. 

For general step-by-step instruction, 
please refer to section [adsl](#standardize_adsl). 

```{r, standardize_adpx}

#-----------------------------------
# standardize_nmdat_data_selector
#-----------------------------------
output$adsl_for_assemble_selector <-renderUI({
  
  # callModule 
  ALL = callModule(module_load_dataset, "load_adsl_for_assemble", 
                   ALL, dataset_name="mYtEsT_for_adsl_assemble", 
                   dataset_type = "adsl")

  # UI  
  fluidRow(column(12, 
                  module_load_dataset_UI(("load_adsl_for_assemble"), label=NULL)
          )
   )  
})

output$adex_for_assemble_selector <-renderUI({
  
  # callModule 
  ALL = callModule(module_load_dataset, "load_adex_for_assemble", 
                     ALL, dataset_name="mYtEsT_for_adex_assemble", 
                   dataset_type = "adex")

  # UI  
  fluidRow(column(12, 
                  module_load_dataset_UI(("load_adex_for_assemble"), label=NULL)
          )
   )  
})

output$adpc_for_assemble_selector <-renderUI({
  
  # callModule 
  ALL = callModule(module_load_dataset, "load_adpc_for_assemble", 
                     ALL, dataset_name="mYtEsT_for_adpc_assemble", 
                   dataset_type = "adpc")

  # UI  
  fluidRow(column(12, 
                  module_load_dataset_UI(("load_adpc_for_assemble"), label=NULL)
          )
   )  
})

output$other_for_assemble_selector <-renderUI({
  
  # callModule 
  ALL = callModule(module_load_dataset, "load_other_for_assemble", 
                     ALL, dataset_name="mYtEsT_for_other_assemble", 
                   dataset_type = "other")

  # UI  
  fluidRow(column(12, 
                  module_load_dataset_UI(("load_other_for_assemble"), label=NULL)
          )
   )  
})

tagList(
  fluidRow(
    column(6, 
           uiOutput(("adsl_for_assemble_selector"))
           ), 
    column(6, 
           uiOutput(("adex_for_assemble_selector"))
    )
  ), 
  fluidRow(
    column(6, 
           uiOutput(("adpc_for_assemble_selector"))
           ), 
    column(6, 
           uiOutput(("other_for_assemble_selector"))
    )
  )
)
 


adsl_for_assemble <- reactive({
  tdata = ALL$DATA[["mYtEsT_for_adsl_assemble"]] 
  
  validate(need(tdata, message="no adsl"))
  tdata %>% build_adsl()
})

adex_for_assemble <- reactive({
  tdata = ALL$DATA[["mYtEsT_for_adex_assemble"]]  
  validate(need(tdata, message="no adex"))

  tdata %>% build_adex()
})

adpc_for_assemble <- reactive({
  tdata = ALL$DATA[["mYtEsT_for_adpc_assemble"]]  
  validate(need(tdata, message="no adpc"))
    
  tdata%>% build_adpc()
}) 

other_for_assemble <- reactive({
  tdata = ALL$DATA[["mYtEsT_for_other_assemble"]] 
    #validate(need(tdata, message="no other"))
   if(!is.null(tdata)) {
     tdata %>% build_adpc()
   }else{
     NULL
   }
})



output$assemble_adsl_adex_adpc_other_container <- renderUI({ 
  # Create a namespace function using the provided id
  #ns <- NS(id)
  
  validate(need(adsl_for_assemble(), message="no adsl found yet"),
           need(adex_for_assemble(), message="no adex found yet"), 
           need(adpc_for_assemble(), message="no adpc found yet") 
           #need(other_for_assemble(), message="no other found yet")
  )
       
    
  script <- list.files(path=paste0(HOME, "/script/"), 
                         full.names = TRUE,
                         pattern="build_adpx")
  names(script) = basename(script)
  
 
  ALL = callModule(module_run_script, "assemble_adsl_adex_adpc_other", 
                   ALL, 
                   dataset= list(adsl = adsl_for_assemble(), 
                                 adex = adex_for_assemble(), 
                                 adpc = adpc_for_assemble(), 
                                 other = other_for_assemble()
                                 ), 
                   script=script)

  

   module_run_script_UI(("assemble_adsl_adex_adpc_other"), label = NULL) 
     
})

 fluidRow(column(12, uiOutput(("assemble_adsl_adex_adpc_other_container"))))
 
 
 
 
```




## Standardize nmdat <a name="standardize_nmdat"></a>

If you have a nonmem-like dataset, but may not be compatible with the format using in this app, 
you may use this subsection to standardize it for subsequent pharmacokinetic analyses. 
  
For general step-by-step instruction, 
please refer to section [adsl](#standardize_adsl). 
  
```{r, standardize_nmdat}

#----------------------------------------------------
# standardize_nmdat
#----------------------------------------------------
# default_adpc_checkin
default_nmdat_checkin <- reactive({ 
  read_excel(paste0(HOME, "/lib/pkmeta.xlsx"),sheet="nmdat",col_names = TRUE)  %>% 
    as.data.frame() %>% filter(!is.na(standard.name))
})

output$standardize_nmdat <-renderUI({
  validate(need(globalVars$login$status, message=FALSE))
  
  script <- list.files(path=paste0(HOME, "/script/"), 
                         full.names = TRUE,
                         pattern="build_nmdat")
  names(script) = basename(script)
  
  # callModule 
  ALL = callModule(module_build_dataset, "standardize_nmdat", 
                   ALL, 
                   dataset_name="mYtEsT_for_standardize_nmdat",
                   script=script,
                   default_checkin= default_nmdat_checkin()
                  )
  

  # UI  
  fluidRow(column(12, 
                   module_build_dataset_UI(id="standardize_nmdat", label=NULL)
                 ) 
          )  
})

fluidRow(column(12, uiOutput(("standardize_nmdat"))))
```

 