
# Report generation 

This chapter is for reviewing all data, tables, figures and models that have been saved through 
the journey of using this handbook, then output those tables and figures, along with their 
titles and footnotes to the corresponding memo/report templates specified by the users. 

## Review
First, review all dataset, figure, table, cppModel, ctlModel and script, modify/delete/save them accordinlgy, then use "Checkout" tab to output them into specified template. 

```{r }

renderUI({ 
    

  callModule(module_review_data, "mydataReview", ALL)
  
  callModule(module_review_figure, "myfigureReview",  ALL)
  
  callModule(module_review_table, "mytableReview",  ALL)
  
  callModule(module_review_cppModel, "mycppModelReview", ALL)
  
  callModule(module_review_ctlModel, "myctlModelReview", ALL)  
  
  callModule(module_review_script, "myscriptReview", ALL)  
    
  callModule(module_check_out, "mycheckOut", ALL)  


  
tabBox(width=12, id = ("review_all"), title =NULL, 
  
  tabPanel(title="Data",  icon = icon("database", lib = "font-awesome"),
          module_review_data_UI(id="mydataReview", label="")
  ), 
  
  tabPanel(title="Figure",  icon = icon("bar-chart-o", lib = "font-awesome"),
           module_review_figure_UI(id="myfigureReview", label="")
  ), 
   
 tabPanel(title="Table", icon = icon("table", lib = "font-awesome"),
          module_review_table_UI(id="mytableReview", label="")
 ),
   
  tabPanel(title="cppModel", icon = icon("motorcycle", lib = "font-awesome"),
           module_review_cppModel_UI(id="mycppModelReview", label="")
  ),

  tabPanel(title="ctlModel", icon = icon("motorcycle", lib = "font-awesome"),
          module_review_ctlModel_UI(id="myctlModelReview", label="")
  ),

  tabPanel(title="script", icon = icon("motorcycle", lib = "font-awesome"),
          module_review_script_UI(id="myscriptReview", label="")
  ),
 
   tabPanel(title="Checkout", 
           module_check_out_UI(id="mycheckOut", label="") 
   )
)  
   

})

```
  
## Reporting

use **ReporteRs** or **officer**


```{r, eval=FALSE}
# http://shiny.rstudio.com/articles/generating-reports.html
# 
# https://stackoverflow.com/questions/34816637/parameterized-rmarkdown-document-on-shiny-application
# 
# http://rmarkdown.rstudio.com/developer_parameterized_reports.html
# 
# 
# http://shiny.rstudio.com/gallery/download-knitr-reports.html
# 
# How to link rmarkdown report with shinyapps to export webapp content in R?
# https://stackoverflow.com/questions/33367154/how-to-link-rmarkdown-report-with-shinyapps-to-export-webapp-content-in-r


```





```{r, eval=FALSE}
   navbarMenu(title="Global option",  #"", 
              #tabsetPanel(type = "tabs",   
              tabPanel(title="ColorSetting"#,  #icon = icon("database", lib = "font-awesome"),
                       #scriptTabUI(id="myscriptTab", label="")  
              ), 
              tabPanel(title="themeSetting"  #icon = icon("database", lib = "font-awesome"),
                       #scriptTabUI(id="myscriptTab", label="")  
              ) 
   )

``` 