
# Report generation 

This chapter is for reviewing all data, tables, figures and models that have been saved through 
the journey of using this handbook, then output those tables and figures, along with their 
titles and footnotes to the corresponding memo/report templates specified by the users. 

## Review
First, review all dataset, figure, table, cppModel, ctlModel and script, modify/delete/save them accordinlgy, then use "Checkout" tab to output them into specified template. 

```{r }

renderUI({ 
    
  callModule(module_review_data, "mydataReview", ALL)
  
  callModule(module_review_figure, "myfigureReview",  ALL)
  
  callModule(module_review_table, "mytableReview",  ALL)
  
  callModule(module_review_cppModel, "mycppModelReview", ALL)
  
  callModule(module_review_ctlModel, "myctlModelReview", ALL)  
  
  callModule(module_review_script, "myscriptReview", ALL)  
    
  callModule(module_review_checkout, "mycheckOut", ALL)  

tabBox(width=12, id = ("review_all"), title =NULL, 
  
  tabPanel(title="Data",  icon = icon("database", lib = "font-awesome"),
          module_review_data_UI(id="mydataReview", label="")
  ), 
  
  tabPanel(title="Figure",  icon = icon("bar-chart-o", lib = "font-awesome"),
           module_review_figure_UI(id="myfigureReview", label="")
  ), 
   
 tabPanel(title="Table", icon = icon("table", lib = "font-awesome"),
          module_review_table_UI(id="mytableReview", label="")
 ),
   
  tabPanel(title="cppModel", icon = icon("motorcycle", lib = "font-awesome"),
           module_review_cppModel_UI(id="mycppModelReview", label="")
  ),

  tabPanel(title="ctlModel", icon = icon("motorcycle", lib = "font-awesome"),
          module_review_ctlModel_UI(id="myctlModelReview", label="")
  ),

  tabPanel(title="script", icon = icon("motorcycle", lib = "font-awesome"),
          module_review_script_UI(id="myscriptReview", label="")
  ),
 
   tabPanel(title="Checkout", 
           module_review_checkout_UI(id="mycheckOut", label="") 
   )
)  
   

})

```
  
## Reporting

use **ReporteRs** or **officer**

Note, the following tabset is used to
1) select dataset (dataset tab),
2) select report template or modify it if needed, select report parameters if any, finally download the report (script tab),
3) render the derived data (data tab), final table (table tab) and figure (figure tab) during report generating.".
 

```{r, eval=FALSE}
# http://shiny.rstudio.com/articles/generating-reports.html
# 
# https://stackoverflow.com/questions/34816637/parameterized-rmarkdown-document-on-shiny-application
# 
# http://rmarkdown.rstudio.com/developer_parameterized_reports.html
# 
# 
# http://shiny.rstudio.com/gallery/download-knitr-reports.html
# 
# How to link rmarkdown report with shinyapps to export webapp content in R?
# https://stackoverflow.com/questions/33367154/how-to-link-rmarkdown-report-with-shinyapps-to-export-webapp-content-in-r


```

```{r}

 
#----------------------------------------------------
# load_nmdat_container
#----------------------------------------------------
output$pk_report_data_selector <-renderUI({
   
  # callModule 
  ALL = callModule(module_load_dataset, "load_nmdat_for_pk_report", 
                     ALL, dataset_name="mYtEsT_for_pk_report")
  
  # UI  
  fluidRow(column(6, 
                   module_load_dataset_UI(id="load_nmdat_for_pk_report", label=NULL)
                 )
            )  
  })
  

```


```{r }
output$select_pk_report_template_container <- renderUI({ 
 script <- list.files(path=paste0(HOME, "/script/"), 
                         full.names = TRUE,
                         pattern="report_template_pk")
  names(script) = basename(script)
  
  selectizeInput(("script_selector"),
                               label    = NULL, #"select script:" ,
                               choices  = names(script),
                               multiple = FALSE,
                               selected = names(script)[1]
                             )
  
})
```


```{r }
output$download_report_container <- renderUI({ 

    
  # callModule

  regFormula <- reactive({
    as.formula(paste('mpg ~', input$x))
  })
  
  # output$regPlot <- renderPlot({
  #   par(mar = c(4, 4, .1, .1))
  #   plot(regFormula(), data = mtcars, pch = 19)
  # })
  
  output$downloadReport <- downloadHandler(
    filename = function() {
      paste('my-report', sep = '.', switch(
        input$format, PDF = 'pdf', HTML = 'html', Word = 'docx'
      ))
    },
    
    content = function(file) {
      src <- normalizePath(paste0(HOME, "/rmd/10_reporting/report_template_pk.Rmd"))
      
      # temporarily switch to the temp dir, in case you do not have write
      # permission to the current working directory
      owd <- setwd(tempdir())
      on.exit(setwd(owd))
      file.copy(src, 'report_template.Rmd', overwrite = TRUE)
      
      library(rmarkdown)
      
      #out <- render_report("report_template.Rmd", input, regFormula, 'sf', 134)
      out <- rmarkdown::render(
        input = 'report_template.Rmd', 
        params = list(
          ALL = ALL, 
          region = "Europe",
          year = 2019
        ),
        output_format = switch(
         input$format,
         PDF = pdf_document(), HTML = html_document(), Word = word_document()
       ))
      
      file.rename(out, file)
    }
  )
    
  # UI
  fluidRow(
    column(6, 
      helpText(),
      selectInput('x', 'Build a regression model of mpg against:',
                  choices = names(mtcars)[-1]),
      radioButtons('format', 'Document format', c( 'Word', 'PDF', 'HTML'),
                   inline = TRUE),
      downloadButton('downloadReport')
    )#,
    #column(9,
    #  plotOutput('regPlot')
    #)
) 
     
})

```

```{r}
output$rmd_content_container <- renderUI({
  validate(need(globalVars$login$status, message=FALSE))
  
  aceEditor(("script_content"), 
            mode="r", 
            value= "sfwsfsfsf", #if (is.null(names(script))) {script} else {script[input$script_selector]}, 
            theme = "crimson_editor",   # chrome
            autoComplete = "enabled",
            height = "1000px", 
            fontSize = 15 
  )
  
})

```


```{r, eval=FALSE}

tabBox(width=12, id = ("generate_report"), title =NULL, 
    
   # dataset_container 
   tabPanel(width=12, title="pk report ", value = "pk_report", collapsible = TRUE, 
            collapsed = TRUE, solidHeader = TRUE,
            
            fluidRow(column(12, uiOutput(("generate_pk_report_container"))))
            
            # fluidRow(
            #          HTML(colFmt(
            #            "Note, 1) select dataset, 
            #                   2) select report template, 
            #                   3) select report parameters if any, 
            #                   4) optional, modify report template, 
            #                   5) download report ", color="gray")
            #          ),
            #   fluidRow(column(width=12, tags$hr(style="border-color: gray;"))),
            #   fluidRow(
            #     column(width=6, uiOutput(("pk_report_data_selector"))),
            #     column(width=6, uiOutput(("select_pk_report_template_container")))
            #     ), 
            #    
            #   fluidRow(column(width=12, tags$hr(style="border-color: gray;"))),
            #   
            #   fluidRow(column(12, uiOutput(("download_report_container")))),
            #   
            #   fluidRow(column(width=12, tags$hr(style="border-color: gray;"))),
            #   
            #   fluidRow(column(12, uiOutput(("rmd_content_container")))), 
            #   
            #   #fluidRow(column(12, uiOutput(ns("render_dataset_container")))), 
            #   style='margin-bottom:30px;  border:1px solid; padding: 10px;'
            # )
   ),
         
    # cppModel_container 
    tabPanel(width=12, title="simulation memo", value = "simulation_memo", collapsible = TRUE, 
            collapsed = TRUE, solidHeader = TRUE,
            fluidRow(
              #fluidRow(column(12, uiOutput(ns("load_cppModel_container")))), 
            style='margin-bottom:30px;  border:1px solid; padding: 10px;'
            )
    ),       
   
       # cppModel_container 
    tabPanel(width=12, title="diagnostic memo", value = "diagnostic_memo", collapsible = TRUE, 
            collapsed = TRUE, solidHeader = TRUE,
            fluidRow(
              #fluidRow(column(12, uiOutput(ns("load_cppModel_container")))), 
            style='margin-bottom:30px;  border:1px solid; padding: 10px;'
            )
    ),       
   
       # cppModel_container 
    tabPanel(width=12, title="popPK report", value = "popPK_report", collapsible = TRUE, 
            collapsed = TRUE, solidHeader = TRUE,
            fluidRow(
              #fluidRow(column(12, uiOutput(ns("load_cppModel_container")))), 
            style='margin-bottom:30px;  border:1px solid; padding: 10px;'
            )
    )  
)
```


 
    

```{r}  
 
output$generate_pk_report_container <- renderUI({ 

  #validate(need(drug_descriptive_analysis_inputData(), message="no data found yet"))
 
  # scripts
  script <- list.files(path=paste0(HOME, "/script/"), 
                         full.names = TRUE,
                         pattern="report_template_pk")
  names(script) = basename(script)
    
  # callModule
  ALL = callModule(module_generate_report, "generate_pk_report", 
                   ALL, key = "report_template_pk")
  
  #, dataset, script, params=NULL
    
  # UI
  module_generate_report_UI(("generate_pk_report"), label = NULL) 
     
})

fluidRow(column(12, uiOutput(("generate_pk_report_container"))))

```


