 
 

## Quick check  
A NONMEM formatted data file is created by using the clinical and bioanalytical databases.   In general, the following rules will be applied.  In particular, a dataset not passing _quick check_ will not be processed further.  To ensure the integrity and traceability of the data, no samples should be deleted, use 'C' to flag samples if needed and specify the reasons in 'CFLAG'.

1) first character of header in nmdat shouldn't be "'"  (write.table, quote=FALSE)
2) EXDUR, RATE can't be negative (due to wrong time in dosing)
3) WGTBL should be cascaded for all rows and subjects;
4) ID shouldn't be too long

 
```{r}  
values <- reactiveValues()

# nmdat_mandatory_check
nmdat_mandatory_check <- function(nmdat, values4nmdat)  {
  validate(need(nmdat, message=FALSE)) 
 
  values4nmdat = check.colnames.in.stdlist(nmdat, col.lst=nmdat.mandatory.var.lst) %>% 
    push_to_values4nmdat(values4nmdat, category="colnames.in.stdlist") 
      
  values4nmdat$mandatory_check = values4nmdat$pass_quick_check  
  
return(values4nmdat)
}

# nmdat_quick_check
nmdat_quick_check <- function(nmdat, values4nmdat)  {
  validate(need(values4nmdat$mandatory_check, message=FALSE)) 
 
  values4nmdat = check.col.in.numint(nmdat)  %>% 
    push_to_values4nmdat(values4nmdat, category="col.in.numint")  
  
  values4nmdat = check.colnames.length.le8(nmdat)  %>% 
    push_to_values4nmdat(values4nmdat, category="colnames.length.le8") 
  
  values4nmdat = check.colnames.uppercase(nmdat)  %>% 
    push_to_values4nmdat(values4nmdat, category="colnames.uppercase") 
  
  values4nmdat = check.colnames.not.start.num(nmdat)  %>% 
    push_to_values4nmdat(values4nmdat, category="colnames.not.start.num") 
  
  values4nmdat = check.label.colnames.lt40(nmdat)  %>% 
    push_to_values4nmdat(values4nmdat, category="label.colnames.lt40") 
  
  values4nmdat = check.obs.order.by.time(nmdat)  %>% 
    push_to_values4nmdat(values4nmdat, category="obs.order.by.time")
  
  values4nmdat = check.missing.ID(nmdat)%>% 
    push_to_values4nmdat(values4nmdat, category="missing.ID")                         
  
  values4nmdat = check.missing.TIME(nmdat)%>% 
    push_to_values4nmdat(values4nmdat, category="missing.TIME") 
  
  values4nmdat = check.missing.MDV(nmdat) %>% 
    push_to_values4nmdat(values4nmdat, category="missing.MDV")
  
  values4nmdat = check.missing.CMT(nmdat) %>% 
    push_to_values4nmdat(values4nmdat, category="missing.CMT") 
  
  values4nmdat = check.inconsistent.DV.MDV(nmdat) %>% 
    push_to_values4nmdat(values4nmdat, category="inconsistent.DV.MDV")    
     
return(values4nmdat)
}
```
 
*** 

<!-- A NONMEM dataset must contain mandatory variables indicated in below table.-->
```{r } 
   
check.colnames.in.stdlist <- function(nmdat, col.lst=NULL)  {
  validate(need(nmdat, message=FALSE))
  status=FALSE; info=""; table=NULL; figure=NULL
   
  YN = col.lst %in% colnames(nmdat)  
  status <- ifelse(all(YN), "green", "red")
  info = paste0(setdiff(col.lst, colnames(nmdat) ), collapse=", ")
  info = colFmt(paste0("Missing key variable in the dataset: ", info, "."),'red')
 
  return(list(status=status, info=info, table=table, figure=figure))
}
 
status <- renderUI({
  category = "colnames.in.stdlist"    
  callModule(module_check_nmdat_status,paste0(category,"_status"), values4nmdat, category)
  div(module_check_nmdat_status_UI(
      id=paste0(category,"_status"),label=NULL ),style="display: inline-block")
})

info <- renderUI({
  category = "colnames.in.stdlist"    
  validate(need(values4nmdat[[category]]$status %in% c("yellow", "red"), message=FALSE))
  callModule(module_check_nmdat_info, paste0(category,"_info"), values4nmdat, category)
  module_check_nmdat_info_UI(id=paste0(category,"_info"),label=NULL) 
})

```

* `r status ` A NONMEM dataset must contain mandatory variables incuding _ROWID_, _ID_, _TIME_, _DV_, _CMT_, _MDV_, _AMT_, _RATE_, _EVID_.  See [Confluence](https://sandboxconfluence.regeneron.com/display/PMx/Data+format). 
    + `r info` 
 
 
*** 
     
<!-- 
#################################################################################
################################################################################# 
All mandatory primary variables except C and CFLAG must be numeric value.
-->  
 
```{r}
check.col.in.numint <- function(nmdat)  {
   validate(need(nmdat, message=FALSE))
  
   status=FALSE; info=""; table=NULL; figure=NULL
   
   col.lst <- setdiff(intersect(nmdat.mandatory.var.lst, colnames(nmdat)), c("C", "CFLAG"))
   YN = sapply(nmdat[, col.lst], typeof) %in% c("double", "integer")  # class
   status <- ifelse(all(YN), "green", "red")
   info = paste0(col.lst[which(!YN)], collapse=", ")
   info = paste0("Colnames, ", info, ", is/are not numeric or integer in the dataset.")
   
   return(list(status=status, info=info, table=table, figure=figure))
}
 
status <- renderUI({
  category = "col.in.numint"    
  callModule(module_check_nmdat_status,paste0(category,"_status"), values4nmdat, category)
  div(module_check_nmdat_status_UI(
      id=paste0(category,"_status"),label=NULL ),style="display: inline-block")
})

info <- renderUI({
  category = "col.in.numint"    
  validate(need(values4nmdat[[category]]$status %in% c("yellow", "red"), message=FALSE))
  callModule(module_check_nmdat_info, paste0(category,"_info"), values4nmdat, category)
  module_check_nmdat_info_UI(id=paste0(category,"_info"),label=NULL) 
})  
 
```
 
  
* `r status ` All mandatory primary variables except C and CFLAG must be integer or numeric, as shown in [Appendix-A](mmmm). 
    + `r info ` 

 
***
  
<!-- 3. The variable names can not exceed 8 characters,  should be in upper case, and can't start with numbers.  -->   

```{r } 

check.colnames.length.le8 <- function(nmdat)  {
  validate(need(nmdat, message=FALSE))
  status=FALSE; info=""; table=NULL; figure=NULL
  
  status = ifelse(all(nchar(colnames(nmdat))<=8), "green", "red")
  info = paste0(colnames(nmdat)[which((nchar(colnames(nmdat))>8))], collapse=", ")
  info = paste0("Length of colnames, ", info, ", greater than 8 characters.")
  
  return(list(status=status, info=info, table=table, figure=figure))
}

status <- renderUI({
  category = "colnames.length.le8"    
  callModule(module_check_nmdat_status,paste0(category,"_status"), values4nmdat, category)
  div(module_check_nmdat_status_UI(
    id=paste0(category,"_status"),label=NULL ),style="display: inline-block")
})

info <- renderUI({
  category = "colnames.length.le8"    
  validate(need(values4nmdat[[category]]$status %in% c("yellow", "red"), message=FALSE))
  callModule(module_check_nmdat_info, paste0(category,"_info"), values4nmdat, category)
  module_check_nmdat_info_UI(id=paste0(category,"_info"),label=NULL) 
})

```

* `r status ` The variable names can not exceed 8 characters.
    + `r info ` 


***

<!-- 3. The variable namesshould be in upper case  -->
```{r } 

check.colnames.uppercase <- function(nmdat)  {
  validate(need(nmdat, message=FALSE))
  status=FALSE; info=""; table=NULL; figure=NULL
  
  YN <- colnames(nmdat)==toupper(colnames(nmdat))
  status = ifelse(all(YN), "green", "red")
  info = paste0(colnames(nmdat)[which(!YN)], collapse=", ")
  info = paste0("Variable name not in upper case: ", info, ".") 
  
  return(list(status=status, info=info, table=table, figure=figure))
}

status <- renderUI({
  category = "colnames.uppercase"    
  callModule(module_check_nmdat_status,paste0(category,"_status"), values4nmdat, category)
  div(module_check_nmdat_status_UI(
    id=paste0(category,"_status"),label=NULL ),style="display: inline-block")
})

info <- renderUI({
  category = "colnames.uppercase"    
  validate(need(values4nmdat[[category]]$status %in% c("yellow", "red"), message=FALSE))
  callModule(module_check_nmdat_info, paste0(category,"_info"), values4nmdat, category)
  module_check_nmdat_info_UI(id=paste0(category,"_info"),label=NULL) 
})

```

* `r status ` The variable names should be in upper case.
    + `r info` 


***
<!-- 3. The variable names can't start with numbers.  -->
```{r } 

check.colnames.not.start.num <- function(nmdat)  {
  validate(need(nmdat, message=FALSE))
  status=FALSE; info=""; table=NULL; figure=NULL
  
  YN <- is.na(substr(colnames(nmdat), 1,1) %>% as_numeric())
  status = ifelse(all(YN), "green", "red")
  info = paste0(colnames(nmdat)[which(!YN)], collapse=", ")
  info = paste0("Variable name can't start with numbers:", info, ".") 
  
  return(list(status=status, info=info, table=table, figure=figure))
}

status <- renderUI({
  category = "colnames.not.start.num"    
  callModule(module_check_nmdat_status,paste0(category,"_status"), values4nmdat, category)
  div(module_check_nmdat_status_UI(
    id=paste0(category,"_status"),label=NULL ),style="display: inline-block")
})

info <- renderUI({
  category = "colnames.not.start.num"    
  validate(need(values4nmdat[[category]]$status %in% c("yellow", "red"), message=FALSE))
  callModule(module_check_nmdat_info, paste0(category,"_info"), values4nmdat, category)
  module_check_nmdat_info_UI(id=paste0(category,"_info"),label=NULL) 
})

```

* `r status ` The variable names can't start with numbers. 
    + `r info ` 


***

<!-- The label for variables can notexceed 40 characters--> 
```{r } 

check.label.colnames.lt40 <- function(nmdat)  {
  validate(need(nmdat, message=FALSE))
  status=FALSE; info=""; table=NULL; figure=NULL
  
   YN = nchar(Hmisc::label(nmdat))<=40
   status <- ifelse(all(YN), "green", "orange")
   info = paste0(Hmisc::label(nmdat)[which(!YN)], collapse=", ")
   info = paste0("Label of variables, ", info, ", greater than 40 characters.")
  
  return(list(status=status, info=info, table=table, figure=figure))
}

status <- renderUI({
  category = "label.colnames.lt40"    
  callModule(module_check_nmdat_status,paste0(category,"_status"), values4nmdat, category)
  div(module_check_nmdat_status_UI(
    id=paste0(category,"_status"),label=NULL ),style="display: inline-block")
})

info <- renderUI({
  category = "label.colnames.lt40"    
  validate(need(values4nmdat[[category]]$status %in% c("yellow", "red"), message=FALSE))
  callModule(module_check_nmdat_info, paste0(category,"_info"), values4nmdat, category)
  module_check_nmdat_info_UI(id=paste0(category,"_info"),label=NULL) 
})

```

* `r status ` The label of variables can not exceed 40 characters.
    + `r info ` 


***

  
<!-- All observations (PK, biomarker and PD) or events within a subject should be ordered by TIME.-->

```{r } 
   
check.obs.order.by.time <- function(nmdat)  {
  validate(need(nmdat, message=FALSE))
  status=FALSE; info=""; table=NULL; figure=NULL
   
  t1 = nmdat %>% group_by(ID) %>% 
    dplyr::mutate(TIME2 = sort(as_numeric(TIME))) %>% 
    dplyr::summarise(YN=all(TIME==TIME2)) %>% arrange(ID) 
  status <- ifelse(all(t1$YN), "green", "red")
  info = paste0(t1[which(!t1$YN), "ID"], collapse=", ") 
  info = paste0("The observations or dose events within suject ID(s),", info, ", are not ordered by TIME.")
 
  return(list(status=status, info=info, table=table, figure=figure))
}
 
status <- renderUI({
  category = "obs.order.by.time"    
  callModule(module_check_nmdat_status,paste0(category,"_status"), values4nmdat, category)
  div(module_check_nmdat_status_UI(
      id=paste0(category,"_status"),label=NULL ),style="display: inline-block")
})

info <- renderUI({
  category = "obs.order.by.time"    
  validate(need(values4nmdat[[category]]$status %in% c("yellow", "red"), message=FALSE))
  callModule(module_check_nmdat_info, paste0(category,"_info"), values4nmdat, category)
  module_check_nmdat_info_UI(id=paste0(category,"_info"),label=NULL) 
})

```

* `r status ` All observations (PK, biomarker and PD) or dose events within a subject have to be ordered by TIME. 
    + `r info` 
 
 
*** 
  
<!-- No missing ID values, all ID must be integer -->

```{r } 
   
check.missing.ID <- function(nmdat)  {
  validate(need(nmdat, message=FALSE))
  status=FALSE; info=""; table=NULL; figure=NULL
   
  status <- ifelse(all(!is.na(as.integer(nmdat$ID))), "green", "red")
  info = paste0(nmdat[which(is.na(as.integer(nmdat$ID))), "ROWID"], collapse=", ") 
  info = paste0("The ID in ROWID(s), ", info, ", is/are missing.") 
 
  return(list(status=status, info=info, table=table, figure=figure))
}
 
status <- renderUI({
  category = "missing.ID"    
  callModule(module_check_nmdat_status,paste0(category,"_status"), values4nmdat, category)
  div(module_check_nmdat_status_UI(
      id=paste0(category,"_status"),label=NULL ),style="display: inline-block")
})

info <- renderUI({
  category = "missing.ID"    
  validate(need(values4nmdat[[category]]$status %in% c("yellow", "red"), message=FALSE))
  callModule(module_check_nmdat_info, paste0(category,"_info"), values4nmdat, category)
  module_check_nmdat_info_UI(id=paste0(category,"_info"),label=NULL) 
})

```

* `r status ` No missing ID values, all ID must be integer. 
    + `r info` 
 
 
*** 



<!-- No missing TIME values, all TIME must be integer -->
  ```{r } 
   
check.missing.TIME <- function(nmdat)  {
  validate(need(nmdat, message=FALSE))
  status=FALSE; info=""; table=NULL; figure=NULL
   
  status <- ifelse(all(!is.na(as.integer(nmdat$TIME))), "green", "red")
  info = paste0(nmdat[which(is.na(as.integer(nmdat$TIME))), "ROWID"], collapse=", ") 
  info = paste0("The TIME in ROWID(s), ", info, ", is/are missing.") 
 
  return(list(status=status, info=info, table=table, figure=figure))
}
 
status <- renderUI({
  category = "missing.TIME"    
  callModule(module_check_nmdat_status,paste0(category,"_status"), values4nmdat, category)
  div(module_check_nmdat_status_UI(
      id=paste0(category,"_status"),label=NULL ),style="display: inline-block")
})

info <- renderUI({
  category = "missing.TIME"    
  validate(need(values4nmdat[[category]]$status %in% c("yellow", "red"), message=FALSE))
  callModule(module_check_nmdat_info, paste0(category,"_info"), values4nmdat, category)
  module_check_nmdat_info_UI(id=paste0(category,"_info"),label=NULL) 
})

```

* `r status ` No missing TIME values, all TIME must be integer. 
    + `r info` 
  

*** 

<!-- No missing MDV values, all MDV must be integer -->

```{r } 
   
check.missing.MDV <- function(nmdat)  {
  validate(need(nmdat, message=FALSE))
  status=FALSE; info=""; table=NULL; figure=NULL
   
  status <- ifelse(all(!is.na(as.integer(nmdat$MDV))), "green", "red")
  info = paste0(nmdat[which(is.na(as.integer(nmdat$MDV))), "ROWID"], collapse=", ") 
  info = paste0("The MDV in ROWID(s), ", info, ", is/are missing.") 
 
  return(list(status=status, info=info, table=table, figure=figure))
}
 
status <- renderUI({
  category = "missing.MDV"    
  callModule(module_check_nmdat_status,paste0(category,"_status"), values4nmdat, category)
  div(module_check_nmdat_status_UI(
      id=paste0(category,"_status"),label=NULL ),style="display: inline-block")
})

info <- renderUI({
  category = "missing.MDV"    
  validate(need(values4nmdat[[category]]$status %in% c("yellow", "red"), message=FALSE))
  callModule(module_check_nmdat_info, paste0(category,"_info"), values4nmdat, category)
  module_check_nmdat_info_UI(id=paste0(category,"_info"),label=NULL) 
})

```

* `r status ` No missing MDV values, all MDV must be integer. 
    + `r info` 
 
 
*** 


<!-- No missing CMT values, all CMT must be integer -->
```{r } 
check.missing.CMT <- function(nmdat)  {
  validate(need(nmdat, message=FALSE))
  status=FALSE; info=""; table=NULL; figure=NULL
   
  status <- ifelse(all(!is.na(as.integer(nmdat$CMT))), "green", "red")
  info = paste0(nmdat[which(is.na(as.integer(nmdat$CMT))), "ROWID"], collapse=", ") 
  info = paste0("The CMT in ROWID(s), ", info, ", is/are missing.") 
 
  return(list(status=status, info=info, table=table, figure=figure))
}
 
status <- renderUI({
  category = "missing.CMT"    
  callModule(module_check_nmdat_status,paste0(category,"_status"), values4nmdat, category)
  div(module_check_nmdat_status_UI(
      id=paste0(category,"_status"),label=NULL ),style="display: inline-block")
})

info <- renderUI({
  category = "missing.CMT"    
  validate(need(values4nmdat[[category]]$status %in% c("yellow", "red"), message=FALSE))
  callModule(module_check_nmdat_info, paste0(category,"_info"), values4nmdat, category)
  module_check_nmdat_info_UI(id=paste0(category,"_info"),label=NULL) 
})

```

* `r status ` No missing CMT values, all CMT must be integer. 
    + `r info` 

***

 

<!--  when DV missing, should set MDV =1. -->
```{r } 
check.inconsistent.DV.MDV <- function(nmdat)  {
  validate(need(nmdat, message=FALSE))
  status=FALSE; info=""; table=NULL; figure=NULL
   
  tabl = nmdat %>% filter(is.na(as_numeric(DV)), as.integer(MDV)==0)  
  status <- ifelse(nrow(tabl)==0, "green", "red")
 
  info = paste0(tabl[, "ROWID"], collapse=", ") 
  info = paste0("Inconsistent DV and MDV found in ROWID(s), ", info, ".")
 
  return(list(status=status, info=info, table=table, figure=figure))
}
 
status <- renderUI({
  category = "inconsistent.DV.MDV"    
  callModule(module_check_nmdat_status,paste0(category,"_status"), values4nmdat, category)
  div(module_check_nmdat_status_UI(
      id=paste0(category,"_status"),label=NULL ),style="display: inline-block")
})

info <- renderUI({
  category = "inconsistent.DV.MDV"    
  validate(need(values4nmdat[[category]]$status %in% c("yellow", "red"), message=FALSE))
  callModule(module_check_nmdat_info, paste0(category,"_info"), values4nmdat, category)
  module_check_nmdat_info_UI(id=paste0(category,"_info"),label=NULL) 
})

```

* `r status ` When DV missing, should set MDV=1. 
    + `r info` 

*** 



```{r}
#<!--   a sammple can be 'missing', can be 'na'(not available), can be BLQ.  -->
 
 
# 
# <!-- 2. No placebo subjects have quantifiable PK measurements.-->
#  
# tabl = nmdat %>% filter(toupper(ARMA)=="PLACEBO", 
#                  TEST==PK.TEST.NAME) %>% group_by(ID, TEST) %>% dplyr::summarise(sumDVOR = sum(as_numeric(abs(DVOR)), na.rm=TRUE)) %>% 
#          filter(sumDVOR>0) %>% ungroup()
# 
# YN = length(tabl$sumDVOR)==0 || tabl$sumDVOR==0
# ```
# 2. `r ifelse(YN, colFmt(asis_output("Yes\U2714"),'green'), colFmt(asis_output("No\U2714"),'red'))` No placebo subjects have quantifiable PK measurements. 
#     
#     
# ```{r placebo.have.quantifiable.PK, anchor="table", tab.cap="The following placebo subjects have quantifiable PK measurements. ", tab.align='center'}
# if (!YN) {kable(nmdat %>% filter(ID %in% tabl$ID, as_numeric(DVOR)>0) %>% select(ID, TEST, NTIM, TIME, DVOR) %>% arrange(ID, TIME, TEST)) }
```





### Summary of quick check
If needed, here summarises all the red alerts if the loaded nonmem data did not pass the _quick check_. You have to fix them before performing further analysis. 

```{r}
# Outputting multiple lines of text with renderText() in R shiny
# https://stackoverflow.com/questions/23233497/outputting-multiple-lines-of-text-with-rendertext-in-r-shiny
renderUI(renderText({
  validate(need(!values4nmdat$pass_quick_check, message=FALSE),   # if not pass
           need( values4nmdat$red_alert, message=FALSE))
    
    info = values4nmdat$red_alert
    info = info[which(!is.null(info) & info!="")]
    info = colFmt(info, "red")
    n = length(info)
    paste0(paste0(1:n, ". ", info), sep = '<br/>')
  })() %>% HTML())

```
 

If needed, here summarises all the yellow alerts captured in checking nonmem data in _quick check_. You may perform further analysis without fixing them. 

```{r}
# Outputting multiple lines of text with renderText() in R shiny
# https://stackoverflow.com/questions/23233497/outputting-multiple-lines-of-text-with-rendertext-in-r-shiny
renderUI(renderText({
  validate(need(values4nmdat$yellow_alert, message=FALSE))   # if not pass
  
    info = values4nmdat$yellow_alert
    info = info[which(!is.null(info) & info!="")]
    info = colFmt(info, "orange")
    n = length(info)
    paste0(paste0(1:n, ". ", info), sep = '<br/>')
  })() %>% HTML())

``` 
  
  
  








 
 
 

 